---
title: "PropIQ — Threshold Analysis"
output:
  flexdashboard::flex_dashboard:
    theme: bootstrap
    orientation: rows
    vertical_layout: scroll
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Barlow+Condensed:wght@400;600;700;800;900&family=Barlow:wght@300;400;500;600;700&family=JetBrains+Mono:wght@400;600&display=swap');

:root {
  --purple-deep:    #0F0720;
  --purple-dark:    #1C0F3A;
  --purple-surface: #2A1650;
  --purple-mid:     #534AB7;
  --purple-muted:   #9B86C0;
  --purple-border:  #2D1A5A;
  --gold:           #F5A623;
  --green:          #2ECC7A;
  --red:            #E85252;
  --white:          #FFFFFF;
}

html, body,
.dashboard-page-wrapper, .dashboard-row,
.chart-wrapper, .chart-stage,
.chart-wrapper-flex, .chart-stage-flex,
.tab-content, .tab-pane,
.nav-tabs-custom > .tab-content {
  background-color: #0F0720 !important;
  background: #0F0720 !important;
}

body {
  color: #FFFFFF !important;
  font-family: 'Barlow', sans-serif !important;
}

/* Navbar */
.navbar, .navbar-inverse {
  background-color: rgba(15,7,32,0.95) !important;
  border-color: #2D1A5A !important;
}
.navbar-inverse .navbar-brand, .navbar-brand {
  color: #F5A623 !important;
  font-weight: 800 !important;
}
.navbar-inverse .navbar-nav > li > a, .navbar-nav > li > a {
  color: #9B86C0 !important;
}
.navbar-inverse .navbar-nav > li > a:hover { color: #FFFFFF !important; }
.navbar-inverse .navbar-nav > .active > a {
  background-color: rgba(83,74,183,0.3) !important;
  color: #F5A623 !important;
}
.dropdown-menu {
  background-color: #1C0F3A !important;
  border-color: #2D1A5A !important;
}
.dropdown-menu > li > a { color: #9B86C0 !important; }
.dropdown-menu > li > a:hover {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
}

/* Pills */
.nav-pills > li > a {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  border: 1px solid #2D1A5A !important;
  border-radius: 6px !important;
  font-size: 13px !important;
  font-weight: 600 !important;
  margin-right: 4px !important;
}
.nav-pills > li > a:hover {
  background-color: #2A1650 !important;
  color: #FFFFFF !important;
  border-color: #534AB7 !important;
}
.nav-pills > li.active > a, .nav-pills > li.active > a:hover {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
  border-color: #534AB7 !important;
}

/* Reactable structural — no cell color overrides */
.rt-table { background-color: #0F0720 !important; }
.rt-thead.-header { background-color: #1C0F3A !important; }
.rt-th {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  font-size: 11px !important;
  font-weight: 600 !important;
  letter-spacing: 0.05em !important;
  text-transform: uppercase !important;
  border-right: 1px solid #2D1A5A !important;
}
.rt-column-group-header {
  background-color: #0F0720 !important;
  border-bottom: 1px solid #2D1A5A !important;
}
.rt-tbody .rt-tr-group { border-bottom: 1px solid #2D1A5A !important; }

/* Sticky cols */
.rt-td-sticky-left {
  background-color: #1C0F3A !important;
  color: #FFFFFF !important;
  border-right: 2px solid #2D1A5A !important;
}
.rt-th-sticky-left {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  border-right: 2px solid #2D1A5A !important;
}

/* Non-colored body cells */
.rt-tbody .rt-td:not([style*="background"]) {
  background-color: #0F0720;
  color: #FFFFFF;
}
.rt-tr-striped .rt-td:not([style*="background"]) {
  background-color: #1C0F3A;
  color: #FFFFFF;
}
.rt-tr-group:hover .rt-td:not([style*="background"]) {
  background-color: #2A1650;
  color: #FFFFFF;
}
.rt-tr-group:hover .rt-td-sticky-left {
  background-color: #2A1650 !important;
  color: #FFFFFF !important;
}

/* Pagination */
.rt-pagination {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  border-top: 1px solid #2D1A5A !important;
}
.rt-page-button {
  background-color: #2A1650 !important;
  color: #9B86C0 !important;
  border: 1px solid #2D1A5A !important;
  border-radius: 4px !important;
}
.rt-page-button:hover { background-color: #534AB7 !important; color: #FFFFFF !important; }
.rt-page-button-current {
  background-color: #F5A623 !important;
  color: #0F0720 !important;
  font-weight: 800 !important;
}

/* Crosstalk filters */
.selectize-control .selectize-input {
  background-color: #1C0F3A !important;
  border: 1px solid #2D1A5A !important;
  color: #FFFFFF !important;
  border-radius: 6px !important;
}
.selectize-dropdown {
  background-color: #1C0F3A !important;
  border: 1px solid #2D1A5A !important;
  color: #FFFFFF !important;
}
.selectize-dropdown .option:hover, .selectize-dropdown .option.active {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
}
label {
  color: #9B86C0 !important;
  font-size: 11px !important;
  font-weight: 600 !important;
  letter-spacing: 0.1em !important;
  text-transform: uppercase !important;
}

/* Scrollbar */
::-webkit-scrollbar { width: 6px; height: 6px; }
::-webkit-scrollbar-track { background: #0F0720; }
::-webkit-scrollbar-thumb { background: #2D1A5A; border-radius: 3px; }
::-webkit-scrollbar-thumb:hover { background: #534AB7; }
```

```{r setup, include=FALSE, echo=FALSE}
color_set <- c("red2", "#f7c844", "#429460")

library(reactable)
library(reactablefmtr)
library(crosstalk)
library(htmltools)
library(scales)
library(glue)

propiq_theme <- reactableTheme(
  color           = "#FFFFFF",
  backgroundColor = "#0F0720",
  borderColor     = "#2D1A5A",
  stripedColor    = "#1C0F3A",
  highlightColor  = "#2A1650",
  cellPadding     = "8px 12px",
  headerStyle = list(
    background    = "#1C0F3A",
    color         = "#9B86C0",
    fontSize      = "11px",
    fontWeight    = "600",
    letterSpacing = "0.05em",
    textTransform = "uppercase",
    borderBottom  = "1px solid #2D1A5A"
  ),
  groupHeaderStyle = list(
    background   = "#0F0720",
    color        = "#9B86C0",
    borderBottom = "1px solid #2D1A5A"
  ),
  paginationStyle = list(
    background = "#1C0F3A",
    color      = "#9B86C0",
    borderTop  = "1px solid #2D1A5A"
  ),
  pageButtonStyle = list(
    background   = "#2A1650",
    color        = "#9B86C0",
    border       = "1px solid #2D1A5A",
    borderRadius = "4px"
  ),
  pageButtonHoverStyle  = list(background = "#534AB7", color = "#FFFFFF"),
  pageButtonActiveStyle = list(background = "#F5A623", color = "#0F0720",
                               fontWeight = "800")
)
```

```{r functions, include=FALSE, echo=FALSE}

# ══════════════════════════════════════════════════════════════════════════════
# build_threshold_table
# Generic table builder for all threshold conditional tables
# ══════════════════════════════════════════════════════════════════════════════

prep_raw_for_threshold <- function(df, player_col, half_col) {
  df |>
    dplyr::rename(player = !!player_col) |>
    dplyr::mutate(
      threshold       = .data[[half_col]],
      threshold_label = as.character(.data[[half_col]])
    )
}



build_threshold_table <- function(data,
                                   prefix,
                                   stat_label,
                                   group_header,
                                   filter_id_base,
                                   period_label) {

  if (nrow(data) == 0) {
    return(htmltools::p(
      style = "color:#9B86C0;font-family:JetBrains Mono,monospace;
               font-size:13px;padding:20px;",
      "No data available for this period and stat."
    ))
  }

  # ── Column identification ──────────────────────────────────────────────────
  fixed_cols <- c("player", "threshold", "threshold_label", "n_games",
                  "Type", "team", "team_logo")
  ou_cols    <- names(data)[grepl(paste0("^", prefix), names(data))]
  ou_cols    <- ou_cols[order(as.numeric(gsub(prefix, "", ou_cols)))]

  if (length(ou_cols) == 0) return(htmltools::p("No OU columns found."))

  # ── Color scale ────────────────────────────────────────────────────────────
  all_values <- unlist(data[, ou_cols], use.names = FALSE)
  all_values <- all_values[!is.na(all_values) & !is.nan(all_values)]
  if (length(all_values) == 0) all_values <- c(0, 1)

  data_min <- min(all_values, na.rm = TRUE)
  data_max <- max(all_values, na.rm = TRUE)
  if (data_min == data_max) { data_min <- data_min - 0.01; data_max <- data_max + 0.01 }

  color_fn <- scales::col_numeric(palette = color_set, domain = c(data_min, data_max))

  # ── OU column defs with color coding ──────────────────────────────────────
  ou_col_defs <- setNames(
    lapply(ou_cols, function(col) {
      num     <- as.numeric(gsub(prefix, "", col))
      ou_name <- paste0(num - 0.5)
      colDef(
        name   = ou_name,
        align  = "center",
        format = colFormat(suffix = "%"),
        style  = function(value) {
          if (is.na(value) || is.nan(value)) return(list())
          bg        <- color_fn(value)
          rgb_vals  <- grDevices::col2rgb(bg) / 255
          luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
          txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
          list(background = bg, color = txt_color,
               fontWeight = "600", borderRadius = "4px", textAlign = "center")
        },
        cell = function(value, index) {
          if (is.na(value) || is.nan(value)) return("—")
          n   <- data$n_games[index]
          num_games <- if (!is.na(n)) round(value * n) else "?"
          htmltools::span(
            title = paste0(num_games, " / ", ifelse(is.na(n), "?", n), " games"),
            style = "cursor:help;border-bottom:1px dotted rgba(255,255,255,0.4);",
            scales::percent(value, accuracy = 1)
          )
        }
      )
    }),
    ou_cols
  )

  col_groups <- list(
    colGroup(
      name        = group_header,
      columns     = ou_cols,
      headerStyle = list(
        background   = "#2e6d9e",
        color        = "#ffffff",
        fontWeight   = "600",
        fontSize     = "13px",
        textAlign    = "center",
        borderRadius = "4px"
      )
    )
  )

  # ── Ensure team columns exist ──────────────────────────────────────────────
  if (!"team"      %in% names(data)) data$team      <- NA_character_
  if (!"team_logo" %in% names(data)) data$team_logo <- NA_character_

  # ── Reorder columns ────────────────────────────────────────────────────────
  col_order <- c("player", "Type", "team_logo", "team",
                 "threshold_label", "n_games",
                 setdiff(names(data), c("player", "Type", "team_logo", "team",
                                         "threshold", "threshold_label", "n_games")))
  col_order <- col_order[col_order %in% names(data)]
  data      <- data[, col_order]

  # ── Fixed column defs ──────────────────────────────────────────────────────
  fixed_col_defs <- list()

  fixed_col_defs[["player"]] <- colDef(
    name        = "Player",
    sticky      = "left",
    width       = 150,
    align       = "left",
    style       = list(fontWeight = "600", color = "#FFFFFF"),
    headerStyle = list(textAlign = "left")
  )

  fixed_col_defs[["Type"]] <- colDef(
    name        = "Split",
    sticky      = "left",
    width       = 130,
    align       = "center",
    style       = list(color = "#FFFFFF", fontSize = "12px"),
    headerStyle = list(textAlign = "center")
  )

  fixed_col_defs[["team_logo"]] <- colDef(
    name     = "",
    sticky   = "left",
    width    = 35,
    align    = "center",
    sortable = FALSE,
    cell     = function(value) {
      if (is.na(value) || nchar(as.character(value)) == 0) return("")
      htmltools::img(src = value, height = "20px", width = "20px",
                     style = "object-fit:contain;")
    }
  )

  fixed_col_defs[["team"]] <- colDef(
    show = FALSE
  )

  fixed_col_defs[["threshold_label"]] <- colDef(
    name        = paste(period_label, stat_label, "≥"),
    sticky      = "left",
    width       = 90,
    align       = "center",
    style       = list(color = "#F5A623", fontWeight = "700", fontSize = "13px"),
    headerStyle = list(textAlign = "center")
  )

  fixed_col_defs[["n_games"]] <- colDef(
    name        = "Games",
    sticky      = "left",
    width       = 65,
    align       = "center",
    style       = list(color = "#FFFFFF", fontSize = "12px"),
    headerStyle = list(textAlign = "center")
  )

  shared_data <- SharedData$new(data)

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    columnGroups        = col_groups,
    highlight           = TRUE,
    striped             = TRUE,
    searchable          = FALSE,
    fullWidth           = TRUE,
    defaultPageSize     = 12,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(12, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    defaultSorted       = list(threshold_label = "asc"),
    theme               = propiq_theme,
    language            = reactableLang(
      pageInfo     = "{rowStart}–{rowEnd} of {rows} rows",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(tagList(
    tags$div(
      style = "display:flex;gap:20px;align-items:flex-end;margin-bottom:16px;flex-wrap:wrap;",

      # Player filter
      tags$div(style = "width:240px;",
        tags$label(
          style = "font-family:sans-serif;font-size:11px;font-weight:600;
                   color:#9B86C0;display:block;margin-bottom:4px;letter-spacing:0.1em;",
          "PLAYER"),
        filter_select(paste0(filter_id_base, "_player"), NULL,
                      shared_data, ~player, multiple = TRUE)
      ),

      # Split filter
      tags$div(style = "width:200px;",
        tags$label(
          style = "font-family:sans-serif;font-size:11px;font-weight:600;
                   color:#9B86C0;display:block;margin-bottom:4px;letter-spacing:0.1em;",
          "SPLIT"),
        filter_select(paste0(filter_id_base, "_type"), NULL,
                      shared_data, ~Type, multiple = TRUE)
      ),

      # Team filter
      tags$div(style = "width:160px;",
        tags$label(
          style = "font-family:sans-serif;font-size:11px;font-weight:600;
                   color:#9B86C0;display:block;margin-bottom:4px;letter-spacing:0.1em;",
          "TEAM"),
        filter_select(paste0(filter_id_base, "_team"), NULL,
                      shared_data, ~team, multiple = TRUE)
      ),

      # Threshold filter
      tags$div(style = "width:160px;",
        tags$label(
          style = "font-family:sans-serif;font-size:11px;font-weight:600;
                   color:#9B86C0;display:block;margin-bottom:4px;letter-spacing:0.1em;",
          paste(period_label, stat_label, "THRESHOLD")),
        filter_select(paste0(filter_id_base, "_thresh"), NULL,
                      shared_data, ~threshold_label, multiple = TRUE)
      )
    ),

    tags$p(
      style = "font-family:JetBrains Mono,monospace;font-size:11px;
               color:#6B4DA0;margin-bottom:12px;",
      paste0("% of games where full game ", tolower(stat_label),
             " hit each O/U line, when player scored ",
             period_label, " ", tolower(stat_label),
             " ≥ threshold. Hover % for fraction.")
    ),

    tbl
  ))
}


# ══════════════════════════════════════════════════════════════════════════════
# build_edge_cards
# Edge card visual for featured players
# ══════════════════════════════════════════════════════════════════════════════

build_edge_cards <- function(data, stat_type, period = "Q1",
                              last_label = NULL) {

  if (nrow(data) == 0) return(htmltools::p(
    style = "color:#9B86C0;font-family:JetBrains Mono,monospace;font-size:13px;padding:20px;",
    "No featured players available."
  ))

  if (is.null(last_label)) {
    last_label <- paste0("L5 Avg ", period, " ",
                         toupper(substr(stat_type, 1, 1)),
                         substr(stat_type, 2, nchar(stat_type)))
  }

  prefix <- paste0("total_", stat_type, "_")

  get_color <- function(pct) {
    if (is.na(pct) || is.nan(pct)) return("#6B4DA0")
    if (pct >= 0.65) return("#2ECC7A")
    if (pct >= 0.50) return("#F5A623")
    return("#E85252")
  }

  get_dynamic_lines <- function(avg_val, stat_type, period) {
    avg_val <- round(avg_val)
    if (stat_type == "pts") {
      offsets <- switch(period,
        "Q1" = list(start=5, step=2, n=6),
        "H1" = list(start=3, step=2, n=5),
        "Q3" = list(start=2, step=1, n=5))
    } else if (stat_type == "ast") {
      offsets <- switch(period,
        "Q1" = list(start=2, step=1, n=5),
        "H1" = list(start=1, step=1, n=4),
        "Q3" = list(start=1, step=1, n=3))
    } else {
      offsets <- switch(period,
        "Q1" = list(start=3, step=1, n=5),
        "H1" = list(start=2, step=1, n=4),
        "Q3" = list(start=1, step=1, n=3))
    }
    start <- avg_val + offsets$start
    as.integer(seq(start, start + (offsets$step*(offsets$n-1)), by=offsets$step))
  }

  cards_html <- purrr::map_chr(seq_len(nrow(data)), function(i) {
    row           <- data[i, ]
    player_name   <- row$player
    avg_val       <- as.numeric(row$avg_last5)
    threshold     <- row$threshold_label
    last_date     <- format(row$last_game_date, "%b %d")
    n_games       <- row$n_games
    team_abbrev   <- if ("team"      %in% names(row) && !is.na(row$team))      row$team      else ""
    team_logo_url <- if ("team_logo" %in% names(row) && !is.na(row$team_logo)) as.character(row$team_logo) else NA_character_
    headshot_url  <- if ("headshot_url" %in% names(row) && !is.na(row$headshot_url)) as.character(row$headshot_url) else NA_character_

    # Avatar
    avatar_html <- if (!is.na(headshot_url)) {
      initials <- paste(substr(strsplit(player_name," ")[[1]],1,1),collapse="") |> substr(1,2)
      glue::glue('
        <img src="{headshot_url}"
             style="width:56px;height:56px;border-radius:50%;object-fit:cover;
                    flex-shrink:0;border:2px solid #2D1A5A;background:#2A1650;"
             onerror="this.onerror=null;this.style.display=\'none\';
                      this.nextElementSibling.style.display=\'flex\';" />
        <div style="display:none;width:56px;height:56px;border-radius:50%;
                    background:#534AB7;align-items:center;justify-content:center;
                    font-family:Barlow Condensed,sans-serif;font-size:18px;
                    font-weight:800;color:#FFFFFF;flex-shrink:0;">{initials}</div>')
    } else {
      initials <- paste(substr(strsplit(player_name," ")[[1]],1,1),collapse="") |> substr(1,2)
      glue::glue('
        <div style="width:56px;height:56px;border-radius:50%;background:#534AB7;
                    display:flex;align-items:center;justify-content:center;
                    font-family:Barlow Condensed,sans-serif;font-size:18px;
                    font-weight:800;color:#FFFFFF;flex-shrink:0;">{initials}</div>')
    }

    # Team display
    team_html <- if (!is.na(team_logo_url)) {
      glue::glue('
        <div style="display:flex;align-items:center;gap:6px;margin-top:4px;">
          <img src="{team_logo_url}" style="width:16px;height:16px;object-fit:contain;"
               onerror="this.style.display=\'none\'" />
          <span style="font-size:11px;color:#F5A623;font-weight:700;
                       font-family:JetBrains Mono,monospace;">{team_abbrev}</span>
        </div>')
    } else if (nchar(team_abbrev) > 0) {
      glue::glue('<span style="font-size:11px;color:#F5A623;font-weight:700;
                  font-family:JetBrains Mono,monospace;margin-top:4px;
                  display:block;">{team_abbrev}</span>')
    } else ""

    # Prop lines
    prop_lines <- get_dynamic_lines(avg_val, stat_type, period)

    lines_html <- purrr::map_chr(prop_lines, function(line) {
      col_name  <- paste0(prefix, line)
      pct       <- if (col_name %in% names(row)) as.numeric(row[[col_name]]) else NA
      if (!is.null(pct) && !is.na(pct) && is.nan(pct)) pct <- NA
      color     <- get_color(pct)
      bar_pct   <- if (!is.na(pct)) round(pct * 100) else 0
      pct_label <- if (!is.na(pct)) paste0(round(pct * 100), "%") else "—"
      ou_label  <- paste0("O ", line - 0.5, " ", stat_type)
      n_num     <- if (!is.na(pct) && !is.na(n_games)) round(pct * as.numeric(n_games)) else "?"
      tooltip   <- paste0(n_num, " / ", n_games, " games")

      glue::glue('
        <div style="display:flex;align-items:center;gap:8px;margin-bottom:6px;"
             title="{tooltip}">
          <div style="font-size:11px;color:#C4AEE8;width:80px;flex-shrink:0;">{ou_label}</div>
          <div style="flex:1;height:6px;background:#2A1650;border-radius:3px;overflow:hidden;">
            <div style="width:{bar_pct}%;height:100%;background:{color};border-radius:3px;"></div>
          </div>
          <div style="font-family:Barlow Condensed,sans-serif;font-size:15px;font-weight:800;
                      color:{color};width:36px;text-align:right;cursor:help;
                      border-bottom:1px dotted rgba(255,255,255,0.3);">{pct_label}</div>
        </div>')
    }) |> paste(collapse = "")

    glue::glue('
      <div style="background:#1C0F3A;border:1px solid #2D1A5A;border-radius:14px;overflow:hidden;">
        <div style="padding:14px 18px;border-bottom:1px solid #2D1A5A;
                    display:flex;align-items:center;gap:12px;">
          {avatar_html}
          <div style="flex:1;min-width:0;">
            <div style="font-size:15px;font-weight:700;color:#FFFFFF;
                        white-space:nowrap;overflow:hidden;text-overflow:ellipsis;">{player_name}</div>
            <div style="font-size:11px;color:#9B86C0;margin-top:3px;">
              {last_label}: <span style="color:#FFFFFF;font-weight:600;">{avg_val}</span>
            </div>
            {team_html}
          </div>
          <div style="background:rgba(245,166,35,0.1);border:1px solid rgba(245,166,35,0.25);
                      border-radius:6px;padding:4px 10px;font-family:JetBrains Mono,monospace;
                      font-size:10px;font-weight:600;color:#F5A623;white-space:nowrap;
                      flex-shrink:0;">{threshold}</div>
        </div>
        <div style="padding:14px 18px;">{lines_html}</div>
      </div>')
  })

  all_cards <- paste(cards_html, collapse = "")

  htmltools::HTML(glue::glue('
    <link href="https://fonts.googleapis.com/css2?family=Barlow+Condensed:wght@700;800;900&family=JetBrains+Mono:wght@400;600&display=swap" rel="stylesheet">
    <div style="background:#0F0720;padding:24px;border-radius:16px;">
      <div style="font-family:JetBrains Mono,monospace;font-size:11px;font-weight:600;
                  color:#F5A623;letter-spacing:0.15em;text-transform:uppercase;margin-bottom:20px;">
        ⚡ {toupper(stat_type)} Edge · {period} L5 Avg Threshold
      </div>
      <div style="display:grid;grid-template-columns:repeat(auto-fill,minmax(300px,1fr));gap:16px;">
        {all_cards}
      </div>
      <div style="margin-top:16px;font-size:11px;color:#6B4DA0;font-family:JetBrains Mono,monospace;">
        🟢 65%+ strong edge · 🟡 50–64% borderline · 🔴 under 50% avoid · hover % for fraction
      </div>
    </div>'))
}


# ══════════════════════════════════════════════════════════════════════════════
# build_edge_explainer
# How to read info button
# ══════════════════════════════════════════════════════════════════════════════

build_edge_explainer <- function(period, stat_type) {
  period_label <- switch(period,
    "Q1" = "first quarter", "H1" = "first half", "Q3" = "first three quarters")
  stat_label <- switch(stat_type,
    "pts" = "points", "ast" = "assists", "reb" = "rebounds")
  button_id <- paste0("info_", period, "_", stat_type)

  htmltools::HTML(glue::glue('
    <div style="margin-bottom:16px;">
      <button onclick="var el=document.getElementById(\'{button_id}\');
                       el.style.display=el.style.display===\'none\'?\'block\':\'none\';"
              style="background:rgba(245,166,35,0.1);border:1px solid rgba(245,166,35,0.3);
                     border-radius:8px;padding:8px 16px;color:#F5A623;
                     font-family:JetBrains Mono,monospace;font-size:11px;font-weight:600;
                     cursor:pointer;letter-spacing:0.05em;">
        ℹ️ HOW TO READ THIS
      </button>
      <div id="{button_id}" style="display:none;margin-top:12px;background:#1C0F3A;
           border:1px solid #2D1A5A;border-radius:12px;padding:16px 20px;
           font-family:Barlow,sans-serif;font-size:13px;color:#C4AEE8;
           line-height:1.7;max-width:680px;">
        <div style="color:#F5A623;font-weight:700;font-size:14px;margin-bottom:10px;">
          📊 {toupper(period)} {toupper(stat_label)} Edge Cards
        </div>
        <p style="margin:0 0 10px 0;">
          Each card shows a featured player and their <strong style="color:#FFFFFF;">
          last 5 game average {period_label} {stat_label}</strong>. This average becomes
          the <strong style="color:#F5A623;">threshold</strong> — we find all games this
          season where they scored <strong style="color:#FFFFFF;">at least that many
          {stat_label}</strong> in the {period_label}, then show how often they hit
          full game O/U lines in those qualifying games.
        </p>
        <p style="margin:0 0 10px 0;">
          <strong style="color:#FFFFFF;">Example:</strong> If a player averages
          4 {stat_label} in the {period_label} over their last 5 games, we find every
          game where they had 4+ {stat_label} in the {period_label} and calculate
          the hit rate for each full game line.
        </p>
        <p style="margin:0 0 6px 0;"><strong style="color:#FFFFFF;">Color guide:</strong></p>
        <div style="display:flex;gap:16px;font-size:12px;">
          <span><span style="color:#2ECC7A;">●</span> 65%+ Strong edge</span>
          <span><span style="color:#F5A623;">●</span> 50–64% Borderline</span>
          <span><span style="color:#E85252;">●</span> Under 50% Avoid</span>
        </div>
        <p style="margin:10px 0 0 0;font-size:11px;color:#6B4DA0;">
          Hover any % to see the exact fraction. Sample includes Regular Season + Playoffs.
        </p>
      </div>
    </div>'))
}

```


Q1 Points {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Q1 Points

```{r edge_q1pts, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("Q1", "pts")
build_edge_cards(actionable_q1_pts_top, "pts", "Q1", "L5 Avg Q1 Pts")
```


Q1 Assists {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Q1 Assists

```{r edge_q1ast, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("Q1", "ast")
build_edge_cards(actionable_q1_ast_top, "ast", "Q1", "L5 Avg Q1 Ast")
```


Q1 Rebounds {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Q1 Rebounds

```{r edge_q1reb, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("Q1", "reb")
build_edge_cards(actionable_q1_reb_top, "reb", "Q1", "L5 Avg Q1 Reb")
```


H1 Points {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### H1 Points

```{r edge_h1pts, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("H1", "pts")
build_edge_cards(actionable_h1_pts_top, "pts", "H1", "L5 Avg H1 Pts")
```


H1 Assists {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### H1 Assists

```{r edge_h1ast, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("H1", "ast")
build_edge_cards(actionable_h1_ast_top, "ast", "H1", "L5 Avg H1 Ast")
```


H1 Rebounds {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### H1 Rebounds

```{r edge_h1reb, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("H1", "reb")
build_edge_cards(actionable_h1_reb_top, "reb", "H1", "L5 Avg H1 Reb")
```


Q3 Points {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Q3 Points

```{r edge_q3pts, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("Q3", "pts")
build_edge_cards(actionable_q3_pts_top, "pts", "Q3", "L5 Avg Q3 Pts")
```


Q3 Assists {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Q3 Assists

```{r edge_q3ast, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("Q3", "ast")
build_edge_cards(actionable_q3_ast_top, "ast", "Q3", "L5 Avg Q3 Ast")
```


Q3 Rebounds {data-navmenu="Tonight's Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Q3 Rebounds

```{r edge_q3reb, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_explainer("Q3", "reb")
build_edge_cards(actionable_q3_reb_top, "reb", "Q3", "L5 Avg Q3 Reb")
```


Points {data-navmenu="Q1 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r q1pts_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = q1_pts_threshold,
  prefix         = "total_pts_",
  stat_label     = "Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_thresh",
  period_label   = "Q1"
)
```

### Raw Detail

```{r q1pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("pts_conditional") && nrow(pts_conditional) > 0) {
  build_threshold_table(
    data           = prep_raw_for_threshold(pts_conditional, "scorer", "fqpts"),
    prefix         = "total_pts_",
    stat_label     = "Pts",
    group_header   = "Full Game Points — Over/Under",
    filter_id_base = "q1pts_raw",
    period_label   = "Q1"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Assists {data-navmenu="Q1 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r q1ast_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = q1_ast_threshold,
  prefix         = "total_ast_",
  stat_label     = "Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q1ast_thresh",
  period_label   = "Q1"
)
```

### Raw Detail

```{r q1ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("ast_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(ast_conditional, "assister", "fqast"),
    prefix         = "total_ast_",
    stat_label     = "Ast",
    group_header   = "Full Game Assists — Over/Under",
    filter_id_base = "q1ast_raw",
    period_label   = "Q1"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Rebounds {data-navmenu="Q1 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r q1reb_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = q1_reb_threshold,
  prefix         = "total_reb_",
  stat_label     = "Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q1reb_thresh",
  period_label   = "Q1"
)
```

### Raw Detail

```{r q1reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("reb_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(reb_conditional, "rebounder", "fqreb"),
    prefix         = "total_reb_",
    stat_label     = "Reb",
    group_header   = "Full Game Rebounds — Over/Under",
    filter_id_base = "q1reb_raw",
    period_label   = "Q1"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Points {data-navmenu="H1 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r h1pts_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = h1_pts_threshold,
  prefix         = "total_pts_",
  stat_label     = "Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "h1pts_thresh",
  period_label   = "H1"
)
```

### Raw Detail

```{r h1pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("h1pts_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(h1pts_conditional, "scorer", "h1pts"),
    prefix         = "total_pts_",
    stat_label     = "Pts",
    group_header   = "Full Game Points — Over/Under",
    filter_id_base = "h1pts_raw",
    period_label   = "H1"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Assists {data-navmenu="H1 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r h1ast_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = h1_ast_threshold,
  prefix         = "total_ast_",
  stat_label     = "Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "h1ast_thresh",
  period_label   = "H1"
)
```

### Raw Detail

```{r h1ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("h1ast_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(h1ast_conditional, "assister", "h1ast"),
    prefix         = "total_ast_",
    stat_label     = "Ast",
    group_header   = "Full Game Assists — Over/Under",
    filter_id_base = "h1ast_raw",
    period_label   = "H1"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Rebounds {data-navmenu="H1 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r h1reb_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = h1_reb_threshold,
  prefix         = "total_reb_",
  stat_label     = "Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "h1reb_thresh",
  period_label   = "H1"
)
```

### Raw Detail

```{r h1reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("h1reb_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(h1reb_conditional, "rebounder", "h1reb"),
    prefix         = "total_reb_",
    stat_label     = "Reb",
    group_header   = "Full Game Rebounds — Over/Under",
    filter_id_base = "h1reb_raw",
    period_label   = "H1"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Points {data-navmenu="Q3 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r q3pts_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = q3_pts_threshold,
  prefix         = "total_pts_",
  stat_label     = "Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q3pts_thresh",
  period_label   = "Q3"
)
```

### Raw Detail

```{r q3pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("q3pts_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(q3pts_conditional, "scorer", "q3pts"),
    prefix         = "total_pts_",
    stat_label     = "Pts",
    group_header   = "Full Game Points — Over/Under",
    filter_id_base = "q3pts_raw",
    period_label   = "Q3"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Assists {data-navmenu="Q3 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r q3ast_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = q3_ast_threshold,
  prefix         = "total_ast_",
  stat_label     = "Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q3ast_thresh",
  period_label   = "Q3"
)
```

### Raw Detail

```{r q3ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("q3ast_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(q3ast_conditional, "assister", "q3ast"),
    prefix         = "total_ast_",
    stat_label     = "Ast",
    group_header   = "Full Game Assists — Over/Under",
    filter_id_base = "q3ast_raw",
    period_label   = "Q3"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```


Rebounds {data-navmenu="Q3 Threshold"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Summary

```{r q3reb_thresh, echo=FALSE, warning=FALSE, message=FALSE}
build_threshold_table(
  data           = q3_reb_threshold,
  prefix         = "total_reb_",
  stat_label     = "Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q3reb_thresh",
  period_label   = "Q3"
)
```

### Raw Detail

```{r q3reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
if (exists("q3reb_conditional")) {
  build_threshold_table(
    data           = prep_raw_for_threshold(q3reb_conditional, "rebounder", "q3reb"),
    prefix         = "total_reb_",
    stat_label     = "Reb",
    group_header   = "Full Game Rebounds — Over/Under",
    filter_id_base = "q3reb_raw",
    period_label   = "Q3"
  )
} else {
  htmltools::p(style="color:#9B86C0;font-family:JetBrains Mono,monospace;padding:20px;",
    "Raw detail not available.")
}
```
