---
title: "Dollar Data Science - Over Hit Rates" 
output: 
  flexdashboard::flex_dashboard:
    theme: flatly
    orientation: rows
    vertical_layout: scroll


---

```{r setup, include=FALSE, echo = FALSE}



color_set <- c("red2","#f7c844","#429460")



```


Points {data-navmenu="Stats" data-navmenu-icon="fa-signal"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------





### Points


```{r pts, echo = FALSE, warning = FALSE, message = FALSE}
# ── Reusable table builder ─────────────────────────────────────────────────────
build_metric_table <- function(pivoted_data, metric_label) {

  fixed_cols <- c("Player", "urlThumbnailTeam", "Type", "metric", "n_games", "avg_min")
  ou_cols    <- setdiff(names(pivoted_data), fixed_cols)
  ou_cols    <- ou_cols[order(as.numeric(ou_cols))]

  all_values <- unlist(pivoted_data[, ou_cols], use.names = FALSE)
  data_min   <- min(all_values, na.rm = TRUE)
  data_max   <- max(all_values, na.rm = TRUE)

  color_fn <- scales::col_numeric(
    palette = color_set,
    domain  = c(data_min, data_max)
  )

  pct_col <- function() {
    colDef(
      align  = "center",
      format = colFormat(suffix = "%"),
      style  = function(value) {
        if (is.na(value)) return(list())
        bg        <- color_fn(value)
        rgb_vals  <- grDevices::col2rgb(bg) / 255
        luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
        txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
        list(
          background   = bg,
          color        = txt_color,
          fontWeight   = "600",
          borderRadius = "4px",
          boxShadow    = "2px 2px 4px rgba(0,0,0,0.15)",
          textAlign    = "center"
        )
      },
      cell = function(value, index, name) {
        if (is.na(value)) return("")
        n         <- pivoted_data$n_games[index]
        num       <- if (!is.na(n)) round(value * n) else "?"
        pct_label <- scales::percent(value, accuracy = 1)
        htmltools::span(
          title = paste0(num, " / ", ifelse(is.na(n), "?", n), " games"),
          style = "cursor: help; border-bottom: 1px dotted #999;",
          pct_label
        )
      }
    )  # ← closes colDef
  }  # ← closes pct_col function

  # ── SharedData must be created before col defs that reference it ─────────────
  shared_data <- SharedData$new(pivoted_data)
  ou_col_defs <- setNames(lapply(ou_cols, function(col) pct_col()), ou_cols)

  # ── Fixed column defs ─────────────────────────────────────────────────────────
  fixed_col_defs <- list(
    Player = colDef(
      sticky      = "left",
      width       = 130,
      align       = "left",
      style       = list(fontWeight = "600"),
      headerStyle = list(textAlign = "left")
    ),
    urlThumbnailTeam = colDef(
      name      = "",
      sticky    = "left",
      width     = 40,
      align     = "center",
      cell      = embed_img(height = "25", width = "25"),
      sortable  = FALSE
    )
  )

  # ── Conditionally add optional columns ────────────────────────────────────────
  if ("n_games" %in% names(pivoted_data)) {
    fixed_col_defs$n_games <- colDef(
      name        = "Games",
      sticky      = "left",
      width       = 70,
      align       = "center",
      headerStyle = list(textAlign = "center"),
      style       = list(color = "#888", fontSize = "12px"),
      format      = colFormat()
    )
  }

  if ("avg_min" %in% names(pivoted_data)) {
    fixed_col_defs$avg_min <- colDef(
      name        = "Avg Min",
      sticky      = "left",
      width       = 75,
      align       = "center",
      headerStyle = list(textAlign = "center"),
      style       = list(color = "#555", fontSize = "12px"),
      format      = colFormat(digits = 1)
    )
  }

  if ("Type" %in% names(pivoted_data)) {
    fixed_col_defs$Type <- colDef(
      name        = "Split",
      sticky      = "left",
      width       = 110,
      align       = "center",
      style       = list(fontWeight = "500", fontSize = "12px", color = "#444"),
      headerStyle = list(textAlign = "center")
    )
  }

  if ("metric" %in% names(pivoted_data)) {
    fixed_col_defs$metric <- colDef(show = FALSE)
  }

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    highlight           = TRUE,
    striped             = TRUE,
    searchable          = FALSE,
    fullWidth           = TRUE,
    defaultPageSize     = 10,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(10, 15, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    theme               = fivethirtyeight(),
    language            = reactableLang(
      pageInfo     = "{rowStart}–{rowEnd} of {rows} players",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(
    tagList(
      tags$div(
        style = "display: flex; gap: 24px; align-items: flex-end; margin-bottom: 16px; flex-wrap: wrap;",
        tags$div(
          style = "width: 250px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "PLAYER"
          ),
          filter_select(
            id         = paste0("player_filter_", tolower(gsub("[^a-z0-9]", "_", metric_label))),
            label      = NULL,
            sharedData = shared_data,
            group      = ~Player,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 200px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "SPLIT"
          ),
          filter_select(
            id         = paste0("type_filter_", tolower(gsub("[^a-z0-9]", "_", metric_label))),
            label      = NULL,
            sharedData = shared_data,
            group      = ~Type,
            multiple   = TRUE
          )
        )
      ),
      tbl
    )
  )
}

# ── Call once per metric ───────────────────────────────────────────────────────
build_metric_table(pt_pivoted, "Points")



```


Assists {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Assists

```{r ast, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(ast_pivoted,  "Assists")
```

Rebounds {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Rebounds

```{r reb, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(reb_pivoted,  "Rebounds")


```


Three Pointers Made {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Three Pointers Made

```{r fg3m, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(fg3m_pivoted,  "Three Pointers Made")




```

Three Pointers Attempted {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Three Pointers Attempted

```{r fg3a, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(fg3a_pivoted,  "Three Pointers Attempted")

```

Steals {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Steals

```{r stl, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(stl_pivoted,  "Steals")

```

Blocks {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Blocks

```{r blk, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(blk_pivoted,  "Blocks")

```

Turnovers {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Turnovers

```{r tov, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(tov_pivoted,  "Turnovers")

```


Free Throws Made {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------
### Free Throws Made

```{r ftm, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(ftm_pivoted,  "Free Throws Made")

```

Field Goals Made {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Field Goals Made

```{r fgm, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(fgm_pivoted,  "Field Goals Made")

```

Points + Rebounds + Assists {data-navmenu="Combo Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Points + Rebounds + Assists


```{r output, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(ptrebast_pivoted,  "Points + Rebounds + Assists")
```

Points + Assists {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Points + Assists


```{r pt_ast, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(pt_ast_pivoted,  "Points + Assists")
```


Points + Rebounds {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Points + Rebounds


```{r pt_reb, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(pt_reb_pivoted,  "Points + Rebounds")
```

Assists + Rebounds {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Assists + Rebounds


```{r ast_reb, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(ast_reb_pivoted,  "Assists + Rebounds")
```

Steals + Blocks {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Steals + Blocks


```{r stl_blk, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(stl_blk_pivoted,  "Steals + Blocks")
```


Points {data-navmenu="First Quarter Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### First Quarter Points


```{r firstqpts, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(firstqpoints_pivoted,  "First Quarter Points")

```


Assists {data-navmenu="First Quarter Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### First Quarter Assists


```{r firstqast, echo = FALSE, warning = FALSE, message = FALSE}


build_metric_table(firstqassists_pivoted,  "First Quarter Assists")



```


Rebounds {data-navmenu="First Quarter Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### First Quarter Rebounds


```{r firstqreb, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(firstqrebounds_pivoted,  "First Quarter Rebounds")


```


Points {data-navmenu="Q1 to Full Game" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================



Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------




### Points


```{r firstqpts_fullgame_bucket, echo = FALSE, warning = FALSE, message = FALSE}


build_conditional_table <- function(
  data           = pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "fqpts",
  prefix         = "total_pts_",
  half_label     = "Q1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_bucket",
  desc_text      = "Rows show bucketed Q1 point totals. Percentages are weighted averages across all games in each bucket."
) {

  fixed_cols <- c(player_col, half_col, "n_games", "Type")
  remaining_cols <- setdiff(names(data), c(player_col, "Type", half_col, "n_games"))
  ou_cols        <- remaining_cols[order(as.numeric(gsub(prefix, "", remaining_cols)))]

  all_values <- unlist(data[, ou_cols], use.names = FALSE)
  data_min   <- min(all_values, na.rm = TRUE)
  data_max   <- max(all_values, na.rm = TRUE)

  color_fn <- scales::col_numeric(
    palette = color_set,
    domain  = c(data_min, data_max)
  )

  ou_col_defs <- setNames(
    lapply(ou_cols, function(col) {
      num     <- as.numeric(gsub(prefix, "", col))
      ou_name <- paste0(num - 0.5)
      colDef(
        name   = ou_name,
        align  = "center",
        format = colFormat(suffix = "%"),
        style  = function(value) {
          if (is.na(value)) return(list())
          bg        <- color_fn(value)
          rgb_vals  <- grDevices::col2rgb(bg) / 255
          luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
          txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
          list(background = bg, color = txt_color,
               fontWeight = "600", borderRadius = "4px", textAlign = "center")
        },
        cell = function(value) {
          if (is.na(value)) return("")
          scales::percent(value, accuracy = 1)
        }
      )
    }),
    ou_cols
  )

  col_groups <- list(
    colGroup(
      name        = group_header,
      columns     = ou_cols,
      headerStyle = list(
        background   = "#2e6d9e",
        color        = "#ffffff",
        fontWeight   = "600",
        fontSize     = "13px",
        textAlign    = "center",
        borderRadius = "4px"
      )
    )
  )

  # Build fixed column defs dynamically using the column name parameters
  fixed_col_defs <- list(
    colDef(
      name        = "Player",
      sticky      = "left",
      width       = 150,
      align       = "left",
      style       = list(fontWeight = "600"),
      headerStyle = list(textAlign = "left")
    ),
    colDef(
      name        = "Split",
      sticky      = "left",
      width       = 130,
      align       = "center",
      style       = list(fontSize = "12px", color = "#444"),
      headerStyle = list(textAlign = "center")
    ),
    colDef(
      name        = half_label,
      sticky      = "left",
      width       = 80,
      align       = "center",
      headerStyle = list(textAlign = "center")
    ),
    colDef(
      name        = "Games",
      sticky      = "left",
      width       = 70,
      align       = "center",
      headerStyle = list(textAlign = "center"),
      style       = list(color = "#888", fontSize = "12px")
    )
  )
  names(fixed_col_defs) <- c(player_col, "Type", half_col, "n_games")
  
  
data <- data |>
  dplyr::select(
    all_of(player_col),
    Type,
    all_of(half_col),
    n_games,
    all_of(remaining_cols)
  )

  shared_data <- SharedData$new(data)

  # Build filter group formulas dynamically
  player_formula <- as.formula(paste0("~", player_col))
  half_formula   <- as.formula(paste0("~", half_col))

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    columnGroups        = col_groups,
    highlight           = TRUE,
    striped             = TRUE,
    searchable          = FALSE,
    fullWidth           = TRUE,
    defaultPageSize     = 15,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(15, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    defaultSorted       = setNames(list("asc"), half_col),
    theme               = fivethirtyeight(),
    language            = reactableLang(
      pageInfo     = "{rowStart}-{rowEnd} of {rows} rows",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(
    tagList(
      tags$div(
        style = "display: flex; gap: 24px; align-items: flex-end; margin-bottom: 16px; flex-wrap: wrap;",
        tags$div(
          style = "width: 250px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "PLAYER"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_player"),
            label      = NULL,
            sharedData = shared_data,
            group      = player_formula,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 200px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            toupper(half_label)
          ),
          filter_select(
            id         = paste0(filter_id_base, "_half"),
            label      = NULL,
            sharedData = shared_data,
            group      = half_formula,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 200px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "SPLIT"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_type"),
            label      = NULL,
            sharedData = shared_data,
            group      = ~Type,
            multiple   = TRUE
          )
        )
      ),
      tags$p(
        style = "font-family: sans-serif; font-size: 12px; color: #888; margin-bottom: 8px;",
        desc_text
      ),
      tbl
    )
  )
}


# ── Bucketed summary table ─────────────────────────────────────────────────────
build_conditional_table(
  data           = pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "fqpts",
  prefix         = "total_pts_",
  half_label     = "Q1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_bucket",
  desc_text      = "Rows show bucketed Q1 point totals. Percentages are weighted averages across all games in each bucket."
)


```

### Raw Detail

```{r q1pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = pts_conditional,
  player_col     = "scorer",
  half_col       = "fqpts",
  prefix         = "total_pts_",
  half_label     = "Q1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_raw",
  desc_text      = "Raw data — each row is an exact Q1 point total."
)
```




Assists {data-navmenu="Q1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------


### Assists


```{r firstqast_fullgame, echo = FALSE, warning = FALSE, message = FALSE}

build_conditional_table(
  data           = ast_conditional_bucketed,
  player_col     = "assister",
  half_col       = "fqast",
  prefix         = "total_ast_",
  half_label     = "Q1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q1ast_bucket",
  desc_text      = "Rows show bucketed Q1 assist totals. Percentages are weighted averages across all games in each bucket."
)

```

### Raw Detail

```{r q1ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = ast_conditional,
  player_col     = "assister",
  half_col       = "fqast",
  prefix         = "total_ast_",
  half_label     = "Q1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q1ast_raw",
  desc_text      = "Raw data — each row is an exact Q1 assist total."
)
```



Rebounds {data-navmenu="Q1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------



### Rebounds


```{r firstqreb_fullgame, echo = FALSE, warning = FALSE, message = FALSE}

build_conditional_table(
  data           = reb_conditional_bucketed,
  player_col     = "rebounder",
  half_col       = "fqreb",
  prefix         = "total_reb_",
  half_label     = "Q1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q1reb_bucket",
  desc_text      = "Rows show bucketed Q1 rebound totals. Percentages are weighted averages across all games in each bucket."
)


```

### Raw Detail

```{r q1reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = reb_conditional,
  player_col     = "rebounder",
  half_col       = "fqreb",
  prefix         = "total_reb_",
  half_label     = "Q1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q1reb_raw",
  desc_text      = "Raw data — each row is an exact Q1 rebound total."
)
```





Points {data-navmenu="H1 to Full Game" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r h1pts_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "h1pts",
  prefix         = "total_pts_",
  half_label     = "H1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "h1pts_bucket",
  desc_text      = "Rows show bucketed H1 point totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r h1pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1pts_conditional,
  player_col     = "scorer",
  half_col       = "h1pts",
  prefix         = "total_pts_",
  half_label     = "H1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "h1pts_raw",
  desc_text      = "Raw data — each row is an exact H1 point total."
)
```


Assists {data-navmenu="H1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Assists

```{r h1ast_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1ast_conditional_bucketed,
  player_col     = "assister",
  half_col       = "h1ast",
  prefix         = "total_ast_",
  half_label     = "H1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "h1ast_bucket",
  desc_text      = "Rows show bucketed H1 assist totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r h1ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1ast_conditional,
  player_col     = "assister",
  half_col       = "h1ast",
  prefix         = "total_ast_",
  half_label     = "H1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "h1ast_raw",
  desc_text      = "Raw data — each row is an exact H1 assist total."
)
```


Rebounds {data-navmenu="H1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Rebounds

```{r h1reb_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1reb_conditional_bucketed,
  player_col     = "rebounder",
  half_col       = "h1reb",
  prefix         = "total_reb_",
  half_label     = "H1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "h1reb_bucket",
  desc_text      = "Rows show bucketed H1 rebound totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r h1reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1reb_conditional,
  player_col     = "rebounder",
  half_col       = "h1reb",
  prefix         = "total_reb_",
  half_label     = "H1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "h1reb_raw",
  desc_text      = "Raw data — each row is an exact H1 rebound total."
)
```



Points {data-navmenu="Q3 to Full Game" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r q3pts_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "q3pts",
  prefix         = "total_pts_",
  half_label     = "Q3 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q3pts_bucket",
  desc_text      = "Rows show bucketed Q1-Q3 point totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r q3pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3pts_conditional,
  player_col     = "scorer",
  half_col       = "q3pts",
  prefix         = "total_pts_",
  half_label     = "Q3 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q3pts_raw",
  desc_text      = "Raw data — each row is an exact Q1-Q3 point total."
)
```


Assists {data-navmenu="Q3 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Assists

```{r q3ast_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3ast_conditional_bucketed,
  player_col     = "assister",
  half_col       = "q3ast",
  prefix         = "total_ast_",
  half_label     = "Q3 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q3ast_bucket",
  desc_text      = "Rows show bucketed Q1-Q3 assist totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r q3ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3ast_conditional,
  player_col     = "assister",
  half_col       = "q3ast",
  prefix         = "total_ast_",
  half_label     = "Q3 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q3ast_raw",
  desc_text      = "Raw data — each row is an exact Q1-Q3 assist total."
)
```


Rebounds {data-navmenu="Q3 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Rebounds

```{r q3reb_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3reb_conditional_bucketed,
  player_col     = "rebounder",
  half_col       = "q3reb",
  prefix         = "total_reb_",
  half_label     = "Q3 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q3reb_bucket",
  desc_text      = "Rows show bucketed Q1-Q3 rebound totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r q3reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3reb_conditional,
  player_col     = "rebounder",
  half_col       = "q3reb",
  prefix         = "total_reb_",
  half_label     = "Q3 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q3reb_raw",
  desc_text      = "Raw data — each row is an exact Q1-Q3 rebound total."
)
```


Points {data-navmenu="Game Day Edge" data-navmenu-icon="fa-signal"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Q1 Points


```{r actionable_q1pts, echo=FALSE, warning=FALSE, message=FALSE}

build_actionable_table <- function(data, player_col, half_col, half_label,
                                   last_col, prefix,
                                   group_header, filter_id_base) {

  ou_cols <- names(data)[grepl(paste0("^", prefix), names(data))]
  ou_cols <- ou_cols[order(as.numeric(gsub(prefix, "", ou_cols)))]

  color_fn <- scales::col_numeric(
    palette = color_set,
    domain  = c(0, 1)
  )

  ou_col_defs <- setNames(
    lapply(ou_cols, function(col) {
      num     <- as.numeric(gsub(prefix, "", col))
      ou_name <- paste0(num - 0.5)
      colDef(
        name   = ou_name,
        align  = "center",
        format = colFormat(suffix = "%"),
        style  = function(value) {
          if (is.na(value)) return(list(background = "#f5f5f5"))
          bg        <- color_fn(value)
          rgb_vals  <- grDevices::col2rgb(bg) / 255
          luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
          txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
          list(background = bg, color = txt_color,
               fontWeight = "600", borderRadius = "4px", textAlign = "center")
        },
        cell = function(value, index) {
          if (is.na(value)) return("—")
          n   <- data$n_games[index]
          num <- if (!is.na(n)) round(value * n) else "?"
          htmltools::span(
            title = paste0(num, " / ", ifelse(is.na(n), "?", n), " games"),
            style = "cursor: help; border-bottom: 1px dotted #999;",
            scales::percent(value, accuracy = 1)
          )
        }
      )
    }),
    ou_cols
  )

  col_groups <- list(
    colGroup(
      name        = group_header,
      columns     = ou_cols,
      headerStyle = list(
        background   = "#2e6d9e",
        color        = "#ffffff",
        fontWeight   = "600",
        fontSize     = "13px",
        textAlign    = "center",
        borderRadius = "4px"
      )
    )
  )

  fixed_col_defs <- list()
  fixed_col_defs[[player_col]] <- colDef(
    name        = "Player",
    sticky      = "left",
    width       = 150,
    align       = "left",
    style       = list(fontWeight = "600"),
    headerStyle = list(textAlign = "left")
  )
  fixed_col_defs[["last_game_date"]] <- colDef(
    name        = "Last Game",
    sticky      = "left",
    width       = 100,
    align       = "center",
    format      = colFormat(date = TRUE),
    headerStyle = list(textAlign = "center")
  )
  fixed_col_defs[[last_col]] <- colDef(
    name        = half_label,
    sticky      = "left",
    width       = 90,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(fontWeight = "700", color = "#2e6d9e")
  )
  fixed_col_defs[["threshold_label"]] <- colDef(
    name        = "Threshold",
    sticky      = "left",
    width       = 100,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(fontSize = "12px", color = "#429460", fontWeight = "600")
  )
  fixed_col_defs[["n_games"]] <- colDef(
    name        = "# of Games",
    sticky      = "left",
    width       = 80,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(color = "#888", fontSize = "12px")
  )

  col_order <- c(
    player_col,
    "last_game_date",
    last_col,
    "threshold_label",
    "n_games",
    setdiff(names(data), c(player_col, "last_game_date",
                            last_col, "threshold_label", "n_games"))
  )
  data <- data[, col_order]

  shared_data <- SharedData$new(data)
  player_formula <- as.formula(paste0("~", player_col))

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    columnGroups        = col_groups,
    highlight           = TRUE,
    striped             = TRUE,
    fullWidth           = TRUE,
    defaultPageSize     = 15,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(15, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    theme               = fivethirtyeight(),
    language            = reactableLang(
      pageInfo     = "{rowStart}-{rowEnd} of {rows} rows",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(
    tagList(
      tags$div(
        style = "display: flex; gap: 24px; align-items: flex-end; margin-bottom: 16px; flex-wrap: wrap;",
        tags$div(
          style = "width: 250px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "PLAYER"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_player"),
            label      = NULL,
            sharedData = shared_data,
            group      = player_formula,
            multiple   = TRUE
          )
        )
      ),
      tags$p(
        style = "font-family: sans-serif; font-size: 12px; color: #888; margin-bottom: 8px;",
        "Hit rates for full game lines when player scores AT LEAST their last game Q1 total. Hover over any percentage to see the fraction."
      ),
      tbl
    )
  )
}

build_actionable_table(
  data           = actionable_q1pts,
  player_col     = "scorer",
  half_col       = "fqpts",
  half_label     = "Last G Q1 Pts",
  last_col       = "last_game_q1pts",
  prefix         = "total_pts_",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "action_q1pts"
)
```

Assists {data-navmenu="Game Day Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------



### Q1 Assists

```{r actionable_q1ast, echo=FALSE, warning=FALSE, message=FALSE}
build_actionable_table(
  data           = actionable_q1ast,
  player_col     = "assister",
  half_col       = "fqast",
  half_label     = "Last G Q1 Ast",
  last_col       = "last_game_q1ast",
  prefix         = "total_ast_",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "action_q1ast"
)
```

Rebounds {data-navmenu="Game Day Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Q1 Rebounds

```{r actionable_q1reb, echo=FALSE, warning=FALSE, message=FALSE}
build_actionable_table(
  data           = actionable_q1reb,
  player_col     = "rebounder",
  half_col       = "fqreb",
  half_label     = "Last G Q1 Reb",
  last_col       = "last_game_q1reb",
  prefix         = "total_reb_",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "action_q1reb"
)
```