---
title: "Prop IQ - Over Hit Rates" 
output: 
  flexdashboard::flex_dashboard:
    theme: flatly
    orientation: rows
    vertical_layout: scroll


---

```{r setup, include=FALSE, echo = FALSE}



color_set <- c("red2","#f7c844","#429460")



```


Points {data-navmenu="Stats" data-navmenu-icon="fa-signal"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------





### Points


```{r pts, echo = FALSE, warning = FALSE, message = FALSE}
# ── Reusable table builder ─────────────────────────────────────────────────────
build_metric_table <- function(pivoted_data, metric_label) {

  fixed_cols <- c("Player", "urlThumbnailTeam", "Type", "metric", "n_games", "avg_min")
  ou_cols    <- setdiff(names(pivoted_data), fixed_cols)
  ou_cols    <- ou_cols[order(as.numeric(ou_cols))]

  all_values <- unlist(pivoted_data[, ou_cols], use.names = FALSE)
  data_min   <- min(all_values, na.rm = TRUE)
  data_max   <- max(all_values, na.rm = TRUE)

  color_fn <- scales::col_numeric(
    palette = color_set,
    domain  = c(data_min, data_max)
  )

  pct_col <- function() {
    colDef(
      align  = "center",
      format = colFormat(suffix = "%"),
      style  = function(value) {
        if (is.na(value)) return(list())
        bg        <- color_fn(value)
        rgb_vals  <- grDevices::col2rgb(bg) / 255
        luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
        txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
        list(
          background   = bg,
          color        = txt_color,
          fontWeight   = "600",
          borderRadius = "4px",
          boxShadow    = "2px 2px 4px rgba(0,0,0,0.15)",
          textAlign    = "center"
        )
      },
      cell = function(value, index, name) {
        if (is.na(value)) return("")
        n         <- pivoted_data$n_games[index]
        num       <- if (!is.na(n)) round(value * n) else "?"
        pct_label <- scales::percent(value, accuracy = 1)
        htmltools::span(
          title = paste0(num, " / ", ifelse(is.na(n), "?", n), " games"),
          style = "cursor: help; border-bottom: 1px dotted #999;",
          pct_label
        )
      }
    )  # ← closes colDef
  }  # ← closes pct_col function

  # ── SharedData must be created before col defs that reference it ─────────────
  shared_data <- SharedData$new(pivoted_data)
  ou_col_defs <- setNames(lapply(ou_cols, function(col) pct_col()), ou_cols)

  # ── Fixed column defs ─────────────────────────────────────────────────────────
  fixed_col_defs <- list(
    Player = colDef(
      sticky      = "left",
      width       = 130,
      align       = "left",
      style       = list(fontWeight = "600"),
      headerStyle = list(textAlign = "left")
    ),
    urlThumbnailTeam = colDef(
      name      = "",
      sticky    = "left",
      width     = 40,
      align     = "center",
      cell      = embed_img(height = "25", width = "25"),
      sortable  = FALSE
    )
  )

  # ── Conditionally add optional columns ────────────────────────────────────────
  if ("n_games" %in% names(pivoted_data)) {
    fixed_col_defs$n_games <- colDef(
      name        = "Games",
      sticky      = "left",
      width       = 70,
      align       = "center",
      headerStyle = list(textAlign = "center"),
      style       = list(color = "#888", fontSize = "12px"),
      format      = colFormat()
    )
  }

  if ("avg_min" %in% names(pivoted_data)) {
    fixed_col_defs$avg_min <- colDef(
      name        = "Avg Min",
      sticky      = "left",
      width       = 75,
      align       = "center",
      headerStyle = list(textAlign = "center"),
      style       = list(color = "#555", fontSize = "12px"),
      format      = colFormat(digits = 1)
    )
  }

  if ("Type" %in% names(pivoted_data)) {
    fixed_col_defs$Type <- colDef(
      name        = "Split",
      sticky      = "left",
      width       = 110,
      align       = "center",
      style       = list(fontWeight = "500", fontSize = "12px", color = "#444"),
      headerStyle = list(textAlign = "center")
    )
  }

  if ("metric" %in% names(pivoted_data)) {
    fixed_col_defs$metric <- colDef(show = FALSE)
  }

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    highlight           = TRUE,
    striped             = TRUE,
    searchable          = FALSE,
    fullWidth           = TRUE,
    defaultPageSize     = 10,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(10, 15, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    theme               = fivethirtyeight(),
    language            = reactableLang(
      pageInfo     = "{rowStart}–{rowEnd} of {rows} players",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(
    tagList(
      tags$div(
        style = "display: flex; gap: 24px; align-items: flex-end; margin-bottom: 16px; flex-wrap: wrap;",
        tags$div(
          style = "width: 250px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "PLAYER"
          ),
          filter_select(
            id         = paste0("player_filter_", tolower(gsub("[^a-z0-9]", "_", metric_label))),
            label      = NULL,
            sharedData = shared_data,
            group      = ~Player,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 200px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "SPLIT"
          ),
          filter_select(
            id         = paste0("type_filter_", tolower(gsub("[^a-z0-9]", "_", metric_label))),
            label      = NULL,
            sharedData = shared_data,
            group      = ~Type,
            multiple   = TRUE
          )
        )
      ),
      tbl
    )
  )
}

# ── Call once per metric ───────────────────────────────────────────────────────
build_metric_table(pt_pivoted, "Points")



```


Assists {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Assists

```{r ast, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(ast_pivoted,  "Assists")
```

Rebounds {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Rebounds

```{r reb, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(reb_pivoted,  "Rebounds")


```


Three Pointers Made {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Three Pointers Made

```{r fg3m, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(fg3m_pivoted,  "Three Pointers Made")




```

Three Pointers Attempted {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Three Pointers Attempted

```{r fg3a, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(fg3a_pivoted,  "Three Pointers Attempted")

```

Steals {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Steals

```{r stl, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(stl_pivoted,  "Steals")

```

Blocks {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Blocks

```{r blk, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(blk_pivoted,  "Blocks")

```

Turnovers {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Turnovers

```{r tov, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(tov_pivoted,  "Turnovers")

```


Free Throws Made {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------
### Free Throws Made

```{r ftm, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(ftm_pivoted,  "Free Throws Made")

```

Field Goals Made {data-navmenu="Stats"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Field Goals Made

```{r fgm, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(fgm_pivoted,  "Field Goals Made")

```

Points + Rebounds + Assists {data-navmenu="Combo Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Points + Rebounds + Assists


```{r output, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(ptrebast_pivoted,  "Points + Rebounds + Assists")
```

Points + Assists {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Points + Assists


```{r pt_ast, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(pt_ast_pivoted,  "Points + Assists")
```


Points + Rebounds {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Points + Rebounds


```{r pt_reb, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(pt_reb_pivoted,  "Points + Rebounds")
```

Assists + Rebounds {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Assists + Rebounds


```{r ast_reb, echo = FALSE, warning = FALSE, message = FALSE}
build_metric_table(ast_reb_pivoted,  "Assists + Rebounds")
```

Steals + Blocks {data-navmenu="Combo Bets"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### Steals + Blocks


```{r stl_blk, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(stl_blk_pivoted,  "Steals + Blocks")
```


Points {data-navmenu="First Quarter Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### First Quarter Points


```{r firstqpts, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(firstqpoints_pivoted,  "First Quarter Points")

```


Assists {data-navmenu="First Quarter Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### First Quarter Assists


```{r firstqast, echo = FALSE, warning = FALSE, message = FALSE}


build_metric_table(firstqassists_pivoted,  "First Quarter Assists")



```


Rebounds {data-navmenu="First Quarter Bets" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------

### First Quarter Rebounds


```{r firstqreb, echo = FALSE, warning = FALSE, message = FALSE}

build_metric_table(firstqrebounds_pivoted,  "First Quarter Rebounds")


```
