---
title: "Prop IQ - Over Hit Rates" 
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    orientation: rows
    vertical_layout: scroll


---

```{css, echo=FALSE}

@import url('https://fonts.googleapis.com/css2?family=Barlow+Condensed:wght@400;600;700;800;900&family=Barlow:wght@300;400;500;600;700&family=JetBrains+Mono:wght@400;600&display=swap');

/* ── PropIQ Color Theme ── */
:root {
  --purple-deep:    #0F0720;
  --purple-dark:    #1C0F3A;
  --purple-surface: #2A1650;
  --purple-mid:     #534AB7;
  --purple-muted:   #9B86C0;
  --purple-border:  #2D1A5A;
  --gold:           #F5A623;
  --gold-light:     #FFD166;
  --green:          #2ECC7A;
  --red:            #E85252;
  --white:          #FFFFFF;
  --text-secondary: #C4AEE8;
  --text-muted:     #6B4DA0;
}

/* ── Body and background ── */
body {
  background-color: #0F0720 !important;
  color: #FFFFFF !important;
  font-family: 'Barlow', sans-serif !important;
}

/* ── Navbar ── */
.navbar {
  background-color: rgba(15,7,32,0.95) !important;
  border-bottom: 1px solid #2D1A5A !important;
}

.navbar-brand {
  color: #F5A623 !important;
  font-weight: 800 !important;
  letter-spacing: 0.5px !important;
}

.navbar-nav > li > a {
  color: #9B86C0 !important;
  font-weight: 500 !important;
}

.navbar-nav > li > a:hover {
  color: #FFFFFF !important;
}

.navbar-nav > .active > a,
.navbar-nav > .active > a:hover {
  background-color: rgba(83,74,183,0.3) !important;
  color: #F5A623 !important;
}

/* ── Dashboard pages and chart wrappers ── */
.dashboard-page-wrapper,
.chart-wrapper,
.chart-stage,
.flexdashboard-page {
  background-color: #0F0720 !important;
}

/* ── Tab pills ── */
.nav-pills > li > a {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  border: 1px solid #2D1A5A !important;
  border-radius: 6px !important;
  font-size: 13px !important;
  font-weight: 600 !important;
  margin-right: 4px !important;
}

.nav-pills > li > a:hover {
  background-color: #2A1650 !important;
  color: #FFFFFF !important;
  border-color: #534AB7 !important;
}

.nav-pills > li.active > a,
.nav-pills > li.active > a:hover {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
  border-color: #534AB7 !important;
}

/* ── Reactable tables ── */
/* Table container */
.rt-table {
  background-color: #0F0720 !important;
}

/* Header */
.rt-thead {
  background-color: #1C0F3A !important;
  border-bottom: 1px solid #2D1A5A !important;
}

.rt-th {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  font-size: 11px !important;
  font-weight: 600 !important;
  letter-spacing: 0.05em !important;
  text-transform: uppercase !important;
  border-right: 1px solid #2D1A5A !important;
}

/* Column group headers */
.rt-column-group-header {
  background-color: #0F0720 !important;
  border-bottom: 1px solid #2D1A5A !important;
}

/* Body rows — only set background, NOT color */
/* This lets the inline color from pct_col() still apply */
.rt-tbody .rt-tr-group {
  border-bottom: 1px solid #2D1A5A !important;
}


/* Sticky left columns specifically */
.rt-td-sticky-left,
.rt-th-sticky-left {
  background-color: #1C0F3A !important;
  color: #FFFFFF !important;
  border-right: 2px solid #2D1A5A !important;
}

/* Pagination */
.rt-pagination {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  border-top: 1px solid #2D1A5A !important;
}

.rt-page-button {
  background-color: #2A1650 !important;
  color: #9B86C0 !important;
  border: 1px solid #2D1A5A !important;
  border-radius: 4px !important;
}

.rt-page-button:hover {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
}

.rt-page-button-current {
  background-color: #F5A623 !important;
  color: #0F0720 !important;
  font-weight: 800 !important;
}

/* Search box */
.rt-search {
  background-color: #1C0F3A !important;
  border: 1px solid #2D1A5A !important;
  color: #FFFFFF !important;
  border-radius: 6px !important;
}

/* ── Reactable pagination ── */
.rt-pagination {
  background-color: #1C0F3A !important;
  color: #9B86C0 !important;
  border-top: 1px solid #2D1A5A !important;
}

.rt-page-button {
  background-color: #2A1650 !important;
  color: #9B86C0 !important;
  border: 1px solid #2D1A5A !important;
  border-radius: 4px !important;
}

.rt-page-button:hover {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
}

.rt-page-button-current {
  background-color: #F5A623 !important;
  color: #0F0720 !important;
  font-weight: 800 !important;
}

/* ── Crosstalk filter dropdowns ── */
.selectize-control .selectize-input {
  background-color: #1C0F3A !important;
  border: 1px solid #2D1A5A !important;
  color: #FFFFFF !important;
  border-radius: 6px !important;
}

.selectize-dropdown {
  background-color: #1C0F3A !important;
  border: 1px solid #2D1A5A !important;
  color: #FFFFFF !important;
}

.selectize-dropdown .option:hover,
.selectize-dropdown .option.active {
  background-color: #534AB7 !important;
  color: #FFFFFF !important;
}

.selectize-dropdown .option.selected {
  background-color: rgba(245,166,35,0.2) !important;
  color: #F5A623 !important;
}

/* ── Filter labels ── */
label {
  color: #9B86C0 !important;
  font-size: 11px !important;
  font-weight: 600 !important;
  letter-spacing: 0.1em !important;
  text-transform: uppercase !important;
}

/* ── Column group headers in reactable ── */
.rt-column-group {
  background-color: #0F0720 !important;
  border-bottom: 1px solid #2D1A5A !important;
}

/* ── Scrollbar styling ── */
::-webkit-scrollbar {
  width: 6px;
  height: 6px;
}

::-webkit-scrollbar-track {
  background: #0F0720;
}

::-webkit-scrollbar-thumb {
  background: #2D1A5A;
  border-radius: 3px;
}

::-webkit-scrollbar-thumb:hover {
  background: #534AB7;
}



/* Fix white background behind pill tabsets */
.tab-content,
.tab-pane,
.tabset-fade,
.nav-tabs-custom,
.chart-wrapper,
.chart-stage {
  background-color: #0F0720 !important;
}

/* The row container behind the pills */
.dashboard-row,
.dashboard-row-container {
  background-color: #0F0720 !important;
}

/* Fix the actual pill tab bar background */
.nav-pills {
  background-color: #0F0720 !important;
  padding: 8px 0 !important;
}

/* Hover — sticky cells specifically need explicit override */
.rt-tr-group:hover .rt-td-sticky-left {
  background-color: #2A1650 !important;
  color: #FFFFFF !important;
}

/* Non-colored body cells default background */
.rt-tbody .rt-td:not([style*="background"]) {
  background-color: #0F0720;
  color: #FFFFFF;
}

/* Striped non-colored cells */
.rt-tr-striped .rt-td:not([style*="background"]) {
  background-color: #1C0F3A;
  color: #FFFFFF;
}

/* Hover non-colored cells */
.rt-tr-group:hover .rt-td:not([style*="background"]) {
  background-color: #2A1650;
  color: #FFFFFF;
}
```

```{r setup, include=FALSE, echo = FALSE}



color_set <- c("red2","#f7c844","#429460")

propiq_theme <- reactableTheme(
  color           = "#FFFFFF",
  backgroundColor = "#0F0720",
  borderColor     = "#2D1A5A",
  stripedColor    = "#1C0F3A",
  highlightColor  = "#2A1650",
  cellPadding     = "8px 12px",
  headerStyle = list(
    background    = "#1C0F3A",
    color         = "#9B86C0",
    fontSize      = "11px",
    fontWeight    = "600",
    letterSpacing = "0.05em",
    textTransform = "uppercase",
    borderBottom  = "1px solid #2D1A5A"
  ),
  groupHeaderStyle = list(
    background  = "#0F0720",
    color       = "#9B86C0",
    borderBottom = "1px solid #2D1A5A"
  ),
  paginationStyle = list(
    background = "#1C0F3A",
    color      = "#9B86C0",
    borderTop  = "1px solid #2D1A5A"
  ),
  pageButtonStyle = list(
    background   = "#2A1650",
    color        = "#9B86C0",
    border       = "1px solid #2D1A5A",
    borderRadius = "4px"
  ),
  pageButtonHoverStyle = list(
    background = "#534AB7",
    color      = "#FFFFFF"
  ),
  pageButtonActiveStyle = list(
    background = "#F5A623",
    color      = "#0F0720",
    fontWeight = "800"
  ),
  # Add these two — they explicitly set the default and striped cell colors
  # at the reactable level before CSS even runs
  rowStyle = list(
    color = "#FFFFFF"
  ),
  rowStripedStyle = list(
    backgroundColor = "#1C0F3A",
    color           = "#FFFFFF"
  )
)

```



Points {data-navmenu="Q1 to Full Game" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================



Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------




### Points


```{r firstqpts_fullgame_bucket, echo = FALSE, warning = FALSE, message = FALSE}


build_conditional_table <- function(
  data           = pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "fqpts",
  prefix         = "total_pts_",
  half_label     = "Q1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_bucket",
  desc_text      = "Rows show bucketed Q1 point totals. Percentages are weighted averages across all games in each bucket."
) {

  fixed_cols <- c(player_col, half_col, "n_games", "Type","team", "team_logo")
  remaining_cols <- setdiff(names(data), fixed_cols)
  
  
  ou_cols <- remaining_cols[
  !is.na(suppressWarnings(as.numeric(gsub(prefix, "", remaining_cols))))
]
ou_cols <- ou_cols[order(as.numeric(gsub(prefix, "", ou_cols)))]

# Guard — if no OU cols found something is wrong
if (length(ou_cols) == 0) {
  stop("No OU columns found in data. Check prefix '", prefix, "' and column names: ",
       paste(names(data), collapse = ", "))
}

all_values <- unlist(data[, ou_cols], use.names = FALSE)
all_values <- all_values[!is.na(all_values)]

# Guard — if all values are NA color scale can't be built
if (length(all_values) == 0) {
  all_values <- c(0, 1)   # fallback domain
}

data_min <- min(all_values, na.rm = TRUE)
data_max <- max(all_values, na.rm = TRUE)

# Guard — if min equals max add small buffer to avoid zero-range domain
if (data_min == data_max) {
  data_min <- data_min - 0.01
  data_max <- data_max + 0.01
}

color_fn <- scales::col_numeric(
  palette = color_set,
  domain  = c(data_min, data_max)
)

  all_values <- unlist(data[, ou_cols], use.names = FALSE)
  data_min   <- min(all_values, na.rm = TRUE)
  data_max   <- max(all_values, na.rm = TRUE)

  color_fn <- scales::col_numeric(
    palette = color_set,
    domain  = c(data_min, data_max)
  )

  ou_col_defs <- setNames(
    lapply(ou_cols, function(col) {
      num     <- as.numeric(gsub(prefix, "", col))
      ou_name <- paste0(num - 0.5)
      colDef(
        name   = ou_name,
        align  = "center",
        format = colFormat(suffix = "%"),
        style  = function(value) {
          if (is.na(value)) return(list())
          bg        <- color_fn(value)
          rgb_vals  <- grDevices::col2rgb(bg) / 255
          luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
          txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
          list(background = bg, color = txt_color,
               fontWeight = "600", borderRadius = "4px", textAlign = "center")
        },
        cell = function(value, index) {
  if (is.na(value)) return("—")
  pct_label <- scales::percent(value, accuracy = 1)
  
  # Show fraction tooltip if n_games exists
  if ("n_games" %in% names(data)) {
    n   <- data$n_games[index]
    num <- if (!is.na(n)) round(value * n) else "?"
    htmltools::span(
      title = paste0(num, " / ", ifelse(is.na(n), "?", n), " games"),
      style = "cursor: help; border-bottom: 1px dotted rgba(255,255,255,0.4);",
      pct_label
    )
  } else {
    htmltools::span(pct_label)
  }
}
      )
    }),
    ou_cols
  )

  col_groups <- list(
    colGroup(
      name        = group_header,
      columns     = ou_cols,
      headerStyle = list(
        background   = "#2e6d9e",
        color        = "#ffffff",
        fontWeight   = "600",
        fontSize     = "13px",
        textAlign    = "center",
        borderRadius = "4px"
      )
    )
  )

  # Build fixed column defs dynamically using the column name parameters
fixed_col_defs <- list(
  colDef(
    name        = "Player",
    sticky      = "left",
    width       = 150,
    align       = "left",
    style       = list(fontWeight = "600", color = "#FFFFFF"),
    headerStyle = list(textAlign = "left")
  ),
  colDef(
    name        = "Split",
    sticky      = "left",
    width       = 130,
    align       = "center",
    style       = list(fontWeight = "600", color = "#FFFFFF"),
    headerStyle = list(textAlign = "center")
  ),
  colDef(
    show = FALSE   # team abbreviation — hidden, used for filter only
  ),
  colDef(
    name        = "Team",
    sticky      = "left",
    width       = 45,
    align       = "center",
    sortable    = FALSE,
    headerStyle = list(textAlign = "center"),
    cell = function(value, index) {
      team_abbrev <- data$team[index]
      if (is.na(value) || nchar(as.character(value)) == 0) {
        return(htmltools::span(
          style = "font-size:10px;font-weight:700;color:#F5A623;",
          team_abbrev
        ))
      }
      htmltools::img(
        src    = value,
        height = "24px",
        width  = "24px",
        style  = "object-fit:contain;",
        title  = team_abbrev
      )
    }
  ),
  colDef(
    name        = half_label,
    sticky      = "left",
    width       = 80,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(color = "#FFFFFF")
  ),
  colDef(
    name        = "Games",
    sticky      = "left",
    width       = 70,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(fontWeight = "600", color = "#FFFFFF")
  )
)

# 6 colDefs need 6 names — player, Type, team (hidden), team_logo, half_col, n_games
names(fixed_col_defs) <- c(player_col, "Type", "team", "team_logo", half_col, "n_games")

# Reorder data columns to match
col_order <- c(
  player_col, "Type", "team", "team_logo", half_col, "n_games",
  setdiff(names(data), c(player_col, "Type", "team", "team_logo", half_col, "n_games"))
)
data <- data[, col_order]

  shared_data <- SharedData$new(data)

  # Build filter group formulas dynamically
  player_formula <- as.formula(paste0("~", player_col))
  half_formula   <- as.formula(paste0("~", half_col))

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    columnGroups        = col_groups,
    highlight           = TRUE,
    striped             = TRUE,
    searchable          = FALSE,
    fullWidth           = TRUE,
    defaultPageSize     = 15,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(15, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    defaultSorted       = setNames(list("asc"), half_col),
    theme               = propiq_theme,
    language            = reactableLang(
      pageInfo     = "{rowStart}-{rowEnd} of {rows} rows",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(
    tagList(
      tags$div(
        style = "display: flex; gap: 24px; align-items: flex-end; margin-bottom: 16px; flex-wrap: wrap;",
        tags$div(
          style = "width: 250px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "PLAYER"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_player"),
            label      = NULL,
            sharedData = shared_data,
            group      = player_formula,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 200px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            toupper(half_label)
          ),
          filter_select(
            id         = paste0(filter_id_base, "_half"),
            label      = NULL,
            sharedData = shared_data,
            group      = half_formula,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 200px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #9B86C0; display: block; margin-bottom: 4px;",
            "SPLIT"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_type"),
            label      = NULL,
            sharedData = shared_data,
            group      = ~Type,
            multiple   = TRUE
          )
        ),
        tags$div(
          style = "width: 180px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #9B86C0; display: block; margin-bottom: 4px;",
            "TEAM"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_team"),
            label      = NULL,
            sharedData = shared_data,
            group      = ~team,
            multiple   = TRUE
          )
        )
      ),
      tags$p(
        style = "font-family: sans-serif; font-size: 12px; color: #888; margin-bottom: 8px;",
        desc_text
      ),
      tbl
    )
  )
}


# ── Bucketed summary table ─────────────────────────────────────────────────────
build_conditional_table(
  data           = pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "fqpts",
  prefix         = "total_pts_",
  half_label     = "Q1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_bucket",
  desc_text      = "Rows show bucketed Q1 point totals. Percentages are weighted averages across all games in each bucket."
)


```

### Raw Detail

```{r q1pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = pts_conditional,
  player_col     = "scorer",
  half_col       = "fqpts",
  prefix         = "total_pts_",
  half_label     = "Q1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q1pts_raw",
  desc_text      = "Raw data — each row is an exact Q1 point total."
)
```




Assists {data-navmenu="Q1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------


### Assists


```{r firstqast_fullgame, echo = FALSE, warning = FALSE, message = FALSE}

build_conditional_table(
  data           = ast_conditional_bucketed,
  player_col     = "assister",
  half_col       = "fqast",
  prefix         = "total_ast_",
  half_label     = "Q1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q1ast_bucket",
  desc_text      = "Rows show bucketed Q1 assist totals. Percentages are weighted averages across all games in each bucket."
)

```

### Raw Detail

```{r q1ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = ast_conditional,
  player_col     = "assister",
  half_col       = "fqast",
  prefix         = "total_ast_",
  half_label     = "Q1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q1ast_raw",
  desc_text      = "Raw data — each row is an exact Q1 assist total."
)
```



Rebounds {data-navmenu="Q1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------



### Rebounds


```{r firstqreb_fullgame, echo = FALSE, warning = FALSE, message = FALSE}

build_conditional_table(
  data           = reb_conditional_bucketed,
  player_col     = "rebounder",
  half_col       = "fqreb",
  prefix         = "total_reb_",
  half_label     = "Q1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q1reb_bucket",
  desc_text      = "Rows show bucketed Q1 rebound totals. Percentages are weighted averages across all games in each bucket."
)


```

### Raw Detail

```{r q1reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = reb_conditional,
  player_col     = "rebounder",
  half_col       = "fqreb",
  prefix         = "total_reb_",
  half_label     = "Q1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q1reb_raw",
  desc_text      = "Raw data — each row is an exact Q1 rebound total."
)
```





Points {data-navmenu="H1 to Full Game" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r h1pts_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "h1pts",
  prefix         = "total_pts_",
  half_label     = "H1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "h1pts_bucket",
  desc_text      = "Rows show bucketed H1 point totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r h1pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1pts_conditional,
  player_col     = "scorer",
  half_col       = "h1pts",
  prefix         = "total_pts_",
  half_label     = "H1 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "h1pts_raw",
  desc_text      = "Raw data — each row is an exact H1 point total."
)
```


Assists {data-navmenu="H1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Assists

```{r h1ast_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1ast_conditional_bucketed,
  player_col     = "assister",
  half_col       = "h1ast",
  prefix         = "total_ast_",
  half_label     = "H1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "h1ast_bucket",
  desc_text      = "Rows show bucketed H1 assist totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r h1ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1ast_conditional,
  player_col     = "assister",
  half_col       = "h1ast",
  prefix         = "total_ast_",
  half_label     = "H1 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "h1ast_raw",
  desc_text      = "Raw data — each row is an exact H1 assist total."
)
```


Rebounds {data-navmenu="H1 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Rebounds

```{r h1reb_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1reb_conditional_bucketed,
  player_col     = "rebounder",
  half_col       = "h1reb",
  prefix         = "total_reb_",
  half_label     = "H1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "h1reb_bucket",
  desc_text      = "Rows show bucketed H1 rebound totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r h1reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = h1reb_conditional,
  player_col     = "rebounder",
  half_col       = "h1reb",
  prefix         = "total_reb_",
  half_label     = "H1 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "h1reb_raw",
  desc_text      = "Raw data — each row is an exact H1 rebound total."
)
```



Points {data-navmenu="Q3 to Full Game" data-navmenu-icon="fa-solid fa-dice-d20"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r q3pts_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3pts_conditional_bucketed,
  player_col     = "scorer",
  half_col       = "q3pts",
  prefix         = "total_pts_",
  half_label     = "Q3 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q3pts_bucket",
  desc_text      = "Rows show bucketed Q1-Q3 point totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r q3pts_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3pts_conditional,
  player_col     = "scorer",
  half_col       = "q3pts",
  prefix         = "total_pts_",
  half_label     = "Q3 Pts",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "q3pts_raw",
  desc_text      = "Raw data — each row is an exact Q1-Q3 point total."
)
```


Assists {data-navmenu="Q3 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Assists

```{r q3ast_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3ast_conditional_bucketed,
  player_col     = "assister",
  half_col       = "q3ast",
  prefix         = "total_ast_",
  half_label     = "Q3 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q3ast_bucket",
  desc_text      = "Rows show bucketed Q1-Q3 assist totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r q3ast_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3ast_conditional,
  player_col     = "assister",
  half_col       = "q3ast",
  prefix         = "total_ast_",
  half_label     = "Q3 Ast",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "q3ast_raw",
  desc_text      = "Raw data — each row is an exact Q1-Q3 assist total."
)
```


Rebounds {data-navmenu="Q3 to Full Game"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Rebounds

```{r q3reb_bucket, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3reb_conditional_bucketed,
  player_col     = "rebounder",
  half_col       = "q3reb",
  prefix         = "total_reb_",
  half_label     = "Q3 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q3reb_bucket",
  desc_text      = "Rows show bucketed Q1-Q3 rebound totals. Percentages are weighted averages across all games in each bucket."
)
```

### Raw Detail

```{r q3reb_raw, echo=FALSE, warning=FALSE, message=FALSE}
build_conditional_table(
  data           = q3reb_conditional,
  player_col     = "rebounder",
  half_col       = "q3reb",
  prefix         = "total_reb_",
  half_label     = "Q3 Reb",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "q3reb_raw",
  desc_text      = "Raw data — each row is an exact Q1-Q3 rebound total."
)
```


Points {data-navmenu="Game Day Edge" data-navmenu-icon="fa-signal"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Q1 Points


```{r actionable_q1pts, echo=FALSE, warning=FALSE, message=FALSE}

build_actionable_table <- function(data, player_col, half_col, half_label,
                                   last_col, prefix,
                                   group_header, filter_id_base) {

  ou_cols <- names(data)[grepl(paste0("^", prefix), names(data))]
  ou_cols <- ou_cols[order(as.numeric(gsub(prefix, "", ou_cols)))]

  color_fn <- scales::col_numeric(
    palette = color_set,
    domain  = c(0, 1)
  )

  ou_col_defs <- setNames(
    lapply(ou_cols, function(col) {
      num     <- as.numeric(gsub(prefix, "", col))
      ou_name <- paste0(num - 0.5)
      colDef(
        name   = ou_name,
        align  = "center",
        format = colFormat(suffix = "%"),
        style  = function(value) {
          if (is.na(value)) return(list(background = "#f5f5f5"))
          bg        <- color_fn(value)
          rgb_vals  <- grDevices::col2rgb(bg) / 255
          luminance <- 0.299 * rgb_vals[1] + 0.587 * rgb_vals[2] + 0.114 * rgb_vals[3]
          txt_color <- if (luminance > 0.5) "#111111" else "#ffffff"
          list(background = bg, color = txt_color,
               fontWeight = "600", borderRadius = "4px", textAlign = "center")
        },
        cell = function(value, index) {
          if (is.na(value)) return("—")
          n   <- data$n_games[index]
          num <- if (!is.na(n)) round(value * n) else "?"
          htmltools::span(
            title = paste0(num, " / ", ifelse(is.na(n), "?", n), " games"),
            style = "cursor: help; border-bottom: 1px dotted #999;",
            scales::percent(value, accuracy = 1)
          )
        }
      )
    }),
    ou_cols
  )

  col_groups <- list(
    colGroup(
      name        = group_header,
      columns     = ou_cols,
      headerStyle = list(
        background   = "#2e6d9e",
        color        = "#ffffff",
        fontWeight   = "600",
        fontSize     = "13px",
        textAlign    = "center",
        borderRadius = "4px"
      )
    )
  )

  fixed_col_defs <- list()
  fixed_col_defs[[player_col]] <- colDef(
    name        = "Player",
    sticky      = "left",
    width       = 150,
    align       = "left",
    style       = list(fontWeight = "600"),
    headerStyle = list(textAlign = "left")
  )
  fixed_col_defs[["last_game_date"]] <- colDef(
    name        = "Last Game",
    sticky      = "left",
    width       = 100,
    align       = "center",
    format      = colFormat(date = TRUE),
    headerStyle = list(textAlign = "center")
  )
  fixed_col_defs[[last_col]] <- colDef(
    name        = half_label,
    sticky      = "left",
    width       = 90,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(fontWeight = "700", color = "#2e6d9e")
  )
  fixed_col_defs[["threshold_label"]] <- colDef(
    name        = "Threshold",
    sticky      = "left",
    width       = 100,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(fontSize = "12px", color = "#429460", fontWeight = "600")
  )
  fixed_col_defs[["n_games"]] <- colDef(
    name        = "# of Games",
    sticky      = "left",
    width       = 80,
    align       = "center",
    headerStyle = list(textAlign = "center"),
    style       = list(color = "#FFFFFF", fontSize = "12px")
  )

  col_order <- c(
    player_col,
    "last_game_date",
    last_col,
    "threshold_label",
    "n_games",
    setdiff(names(data), c(player_col, "last_game_date",
                            last_col, "threshold_label", "n_games"))
  )
  data <- data[, col_order]

  shared_data <- SharedData$new(data)
  player_formula <- as.formula(paste0("~", player_col))

  tbl <- reactable(
    shared_data,
    columns             = c(fixed_col_defs, ou_col_defs),
    columnGroups        = col_groups,
    highlight           = TRUE,
    striped             = TRUE,
    fullWidth           = TRUE,
    defaultPageSize     = 15,
    showPageSizeOptions = TRUE,
    pageSizeOptions     = c(15, 25, 50),
    paginationType      = "jump",
    showPageInfo        = TRUE,
    theme               = fivethirtyeight(),
    language            = reactableLang(
      pageInfo     = "{rowStart}-{rowEnd} of {rows} rows",
      pagePrevious = "← Prev",
      pageNext     = "Next →"
    )
  )

  browsable(
    tagList(
      tags$div(
        style = "display: flex; gap: 24px; align-items: flex-end; margin-bottom: 16px; flex-wrap: wrap;",
        tags$div(
          style = "width: 250px;",
          tags$label(
            style = "font-family: sans-serif; font-size: 12px; font-weight: 600; color: #666; display: block; margin-bottom: 4px;",
            "PLAYER"
          ),
          filter_select(
            id         = paste0(filter_id_base, "_player"),
            label      = NULL,
            sharedData = shared_data,
            group      = player_formula,
            multiple   = TRUE
          )
        )
      ),
      tags$p(
        style = "font-family: sans-serif; font-size: 12px; color: #888; margin-bottom: 8px;",
        "Hit rates for full game lines when player scores AT LEAST their last game Q1 total. Hover over any percentage to see the fraction."
      ),
      tbl
    )
  )
}

build_actionable_table(
  data           = actionable_q1pts,
  player_col     = "scorer",
  half_col       = "fqpts",
  half_label     = "Last G Q1 Pts",
  last_col       = "last_game_q1pts",
  prefix         = "total_pts_",
  group_header   = "Full Game Points — Over/Under",
  filter_id_base = "action_q1pts"
)
```

Assists {data-navmenu="Game Day Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------



### Q1 Assists

```{r actionable_q1ast, echo=FALSE, warning=FALSE, message=FALSE}
build_actionable_table(
  data           = actionable_q1ast,
  player_col     = "assister",
  half_col       = "fqast",
  half_label     = "Last G Q1 Ast",
  last_col       = "last_game_q1ast",
  prefix         = "total_ast_",
  group_header   = "Full Game Assists — Over/Under",
  filter_id_base = "action_q1ast"
)
```

Rebounds {data-navmenu="Game Day Edge"}
=======================================================================

Row {data-height=1000}
-----------------------------------------------------------------------


### Q1 Rebounds

```{r actionable_q1reb, echo=FALSE, warning=FALSE, message=FALSE}
build_actionable_table(
  data           = actionable_q1reb,
  player_col     = "rebounder",
  half_col       = "fqreb",
  half_label     = "Last G Q1 Reb",
  last_col       = "last_game_q1reb",
  prefix         = "total_reb_",
  group_header   = "Full Game Rebounds — Over/Under",
  filter_id_base = "action_q1reb"
)
```



Q1 {data-navmenu="Test" data-navmenu-icon="fa-signal"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r edge_cards_pts, echo=FALSE, warning=FALSE, message=FALSE}


build_edge_explainer <- function(player_col, period, stat_type) {

  period_label <- switch(period,
    "Q1" = "first quarter",
    "H1" = "first half",
    "Q3" = "first three quarters"
  )

  stat_label <- switch(stat_type,
    "pts" = "points",
    "ast" = "assists",
    "reb" = "rebounds"
  )

  button_id <- paste0("info_", period, "_", stat_type)

  htmltools::HTML(glue::glue('
    <div style="margin-bottom:16px;">

      <button onclick="
        var el = document.getElementById(\'{button_id}\');
        el.style.display = el.style.display === \'none\' ? \'block\' : \'none\';
      "
        style="background:rgba(245,166,35,0.1);border:1px solid rgba(245,166,35,0.3);
               border-radius:8px;padding:8px 16px;color:#F5A623;
               font-family:JetBrains Mono,monospace;font-size:11px;font-weight:600;
               cursor:pointer;letter-spacing:0.05em;">
        ℹ️ HOW TO READ THIS
      </button>

      <div id="{button_id}" style="display:none;margin-top:12px;
           background:#1C0F3A;border:1px solid #2D1A5A;border-radius:12px;
           padding:16px 20px;font-family:Barlow,sans-serif;font-size:13px;
           color:#C4AEE8;line-height:1.7;max-width:680px;">

        <div style="color:#F5A623;font-weight:700;font-size:14px;margin-bottom:10px;">
          📊 Understanding the {toupper(period)} {toupper(stat_label)} Edge Cards
        </div>

        <p style="margin:0 0 10px 0;">
          Each card shows a featured player and their <strong style="color:#FFFFFF;">
          last 5 game average {period_label} {stat_label}</strong>. This average
          is used as a <strong style="color:#F5A623;">threshold</strong> — we then
          look at all games this season (Regular Season + Playoffs) where that player
          scored <strong style="color:#FFFFFF;">at least that many {stat_label}
          </strong> in the {period_label}.
        </p>

        <p style="margin:0 0 10px 0;">
          The <strong style="color:#FFFFFF;">percentage bars</strong> show how often
          the player hit each full-game over/under line in those qualifying games.
          The badge in the top right (e.g. <span style="color:#F5A623;">4+ Q1 Pts</span>)
          is the exact threshold being applied.
        </p>

        <p style="margin:0 0 10px 0;"><strong style="color:#FFFFFF;">Example:</strong>
          If a player averages <strong style="color:#FFFFFF;">4 {stat_label}</strong>
          in the {period_label} over their last 5 games, we find every game this
          season where they had 4+ {stat_label} in the {period_label}, then calculate
          how often they hit each full-game line in those games.
        </p>

        <p style="margin:0 0 6px 0;"><strong style="color:#FFFFFF;">Color guide:</strong></p>
        <div style="display:flex;gap:16px;font-size:12px;">
          <span><span style="color:#2ECC7A;">●</span> 65%+ Strong edge</span>
          <span><span style="color:#F5A623;">●</span> 50–64% Borderline</span>
          <span><span style="color:#E85252;">●</span> Under 50% Avoid</span>
        </div>

        <p style="margin:10px 0 0 0;font-size:11px;color:#6B4DA0;">
          Hover over any percentage to see the exact fraction (e.g. 14/18 games).
          Sample size shown as "# of Games" reflects qualifying games only.
        </p>

      </div>
    </div>
  '))
}



build_edge_cards <- function(data, player_col, last_col, threshold_label_col,
                              prefix, title_label, stat_type,
                              period = "Q1",
                              last_label = NULL) {   # ← add last_label param

  # Default label if not provided
  if (is.null(last_label)) {
    last_label <- paste0("L5 Avg ", toupper(period), " ", toupper(title_label))
  }

  get_color <- function(pct) {
    if (is.na(pct)) return("#6B4DA0")
    if (pct >= 0.65) return("#2ECC7A")
    if (pct >= 0.50) return("#F5A623")
    return("#E85252")
  }

  get_dynamic_lines <- function(avg_val, stat_type, period) {
    avg_val <- round(avg_val)
    if (stat_type == "pts") {
      offsets <- switch(period,
        "Q1" = list(start=5, step=2, n=6),
        "H1" = list(start=3, step=2, n=5),
        "Q3" = list(start=2, step=1, n=5)
      )
    } else if (stat_type == "ast") {
      offsets <- switch(period,
        "Q1" = list(start=2, step=1, n=5),
        "H1" = list(start=1, step=1, n=4),
        "Q3" = list(start=1, step=1, n=3)
      )
    } else if (stat_type == "reb") {
      offsets <- switch(period,
        "Q1" = list(start=3, step=1, n=5),
        "H1" = list(start=2, step=1, n=4),
        "Q3" = list(start=1, step=1, n=3)
      )
    }
    start <- avg_val + offsets$start
    as.integer(seq(start, start + (offsets$step*(offsets$n-1)), by=offsets$step))
  }

  cards_html <- purrr::map_chr(seq_len(nrow(data)), function(i) {

    row       <- data[i, ]
    player    <- row[[player_col]]
    last_val  <- round(as.numeric(row[[last_col]]), 1)
    threshold <- row[[threshold_label_col]]
    last_date <- format(row$last_game_date, "%b %d")
    n_games   <- if ("n_games" %in% names(row)) row$n_games else "?"

    # ── Team logo ─────────────────────────────────────────────────────────────
    team_abbrev <- if ("team" %in% names(row) && !is.na(row$team)) row$team else ""
    team_logo   <- if ("team_logo" %in% names(row) && !is.na(row$team_logo)) {
      as.character(row$team_logo)
    } else NA_character_

    team_html <- if (!is.na(team_logo)) {
      glue::glue('
        <div style="display:flex;align-items:center;gap:6px;margin-top:4px;">
          <img src="{team_logo}"
               style="width:18px;height:18px;object-fit:contain;"
               onerror="this.style.display=\'none\'"/>
          <span style="font-size:11px;color:#F5A623;font-weight:700;
                       font-family:JetBrains Mono,monospace;">{team_abbrev}</span>
        </div>
      ')
    } else if (nchar(team_abbrev) > 0) {
      glue::glue('
        <span style="font-size:11px;color:#F5A623;font-weight:700;
                     font-family:JetBrains Mono,monospace;margin-top:4px;
                     display:block;">{team_abbrev}</span>
      ')
    } else ""

    # ── Headshot ──────────────────────────────────────────────────────────────
    headshot_url <- if ("headshot_url" %in% names(row) &&
                        !is.na(row$headshot_url) &&
                        nchar(as.character(row$headshot_url)) > 0) {
      as.character(row$headshot_url)
    } else NA_character_

    avatar_html <- if (!is.na(headshot_url)) {
      glue::glue('
        <img src="{headshot_url}"
             style="width:56px;height:56px;border-radius:50%;
                    object-fit:cover;flex-shrink:0;
                    border:2px solid #2D1A5A;background:#2A1650;"
             onerror="this.onerror=null;this.style.display=\'none\';
                      this.nextElementSibling.style.display=\'flex\';"
        />
        <div style="display:none;width:56px;height:56px;border-radius:50%;
                    background:#534AB7;align-items:center;justify-content:center;
                    font-family:Barlow Condensed,sans-serif;font-size:18px;
                    font-weight:800;color:#FFFFFF;flex-shrink:0;">
          {paste(substr(strsplit(player," ")[[1]],1,1),collapse="") |> substr(1,2)}
        </div>
      ')
    } else {
      initials <- paste(substr(strsplit(player," ")[[1]],1,1),collapse="") |> substr(1,2)
      glue::glue('
        <div style="width:56px;height:56px;border-radius:50%;
                    background:#534AB7;display:flex;align-items:center;
                    justify-content:center;font-family:Barlow Condensed,sans-serif;
                    font-size:18px;font-weight:800;color:#FFFFFF;flex-shrink:0;">
          {initials}
        </div>
      ')
    }

    # ── Dynamic prop lines ────────────────────────────────────────────────────
    prop_lines <- get_dynamic_lines(as.numeric(last_val), stat_type, period)

    lines_html <- purrr::map_chr(prop_lines, function(line) {
      col_name  <- paste0(prefix, line)
      pct       <- if (col_name %in% names(row)) as.numeric(row[[col_name]]) else NA
      color     <- get_color(pct)
      bar_pct   <- if (!is.na(pct)) round(pct * 100) else 0
      pct_label <- if (!is.na(pct)) paste0(round(pct * 100), "%") else "—"
      ou_label  <- paste0("O ", line - 0.5, " ", title_label)

      # Tooltip showing fraction
      n_num     <- if (!is.na(pct) && !is.na(n_games)) round(pct * as.numeric(n_games)) else "?"
      tooltip   <- paste0(n_num, " / ", n_games, " games")

      glue::glue('
        <div style="display:flex;align-items:center;gap:8px;margin-bottom:6px;"
             title="{tooltip}">
          <div style="font-size:11px;color:#C4AEE8;width:80px;flex-shrink:0;">
            {ou_label}
          </div>
          <div style="flex:1;height:6px;background:#2A1650;border-radius:3px;overflow:hidden;">
            <div style="width:{bar_pct}%;height:100%;background:{color};border-radius:3px;"></div>
          </div>
          <div style="font-family:Barlow Condensed,sans-serif;font-size:15px;
                      font-weight:800;color:{color};width:36px;text-align:right;
                      cursor:help;border-bottom:1px dotted rgba(255,255,255,0.3);">
            {pct_label}
          </div>
        </div>
      ')
    }) |> paste(collapse = "")

    glue::glue('
      <div style="background:#1C0F3A;border:1px solid #2D1A5A;border-radius:14px;
                  overflow:hidden;">
        <div style="padding:14px 18px;border-bottom:1px solid #2D1A5A;
                    display:flex;align-items:center;gap:12px;">
          {avatar_html}
          <div style="flex:1;min-width:0;">
            <div style="font-size:15px;font-weight:700;color:#FFFFFF;
                        white-space:nowrap;overflow:hidden;text-overflow:ellipsis;">
              {player}
            </div>
            <div style="font-size:11px;color:#9B86C0;margin-top:3px;">
              {last_label}: <span style="color:#FFFFFF;font-weight:600;">{last_val}</span>
            </div>
            {team_html}
          </div>
          <div style="background:rgba(245,166,35,0.1);
                      border:1px solid rgba(245,166,35,0.25);
                      border-radius:6px;padding:4px 10px;
                      font-family:JetBrains Mono,monospace;
                      font-size:10px;font-weight:600;color:#F5A623;
                      white-space:nowrap;flex-shrink:0;">
            {threshold}
          </div>
        </div>
        <div style="padding:14px 18px;">
          {lines_html}
        </div>
      </div>
    ')
  })

  all_cards <- paste(cards_html, collapse = "")

  htmltools::HTML(glue::glue('
    <link href="https://fonts.googleapis.com/css2?family=Barlow+Condensed:wght@700;800;900&family=JetBrains+Mono:wght@400;600&display=swap" rel="stylesheet">
    <div style="background:#0F0720;padding:24px;border-radius:16px;">
      <div style="font-family:JetBrains Mono,monospace;font-size:11px;font-weight:600;
                  color:#F5A623;letter-spacing:0.15em;text-transform:uppercase;
                  margin-bottom:20px;">
        ⚡ {title_label} Edge · {period} Threshold
      </div>
      <div style="display:grid;grid-template-columns:repeat(auto-fill,minmax(320px,1fr));gap:16px;">
        {all_cards}
      </div>
      <div style="margin-top:16px;font-size:11px;color:#6B4DA0;
                  font-family:JetBrains Mono,monospace;">
        🟢 65%+ strong edge · 🟡 50–64% borderline · 🔴 under 50% avoid ·
        hover any % to see fraction
      </div>
    </div>
  '))
}

build_edge_explainer(
  player_col = "scorer",
  period     = "Q1",
  stat_type  = "pts"
)

# ── Points cards ───────────────────────────────────────────────────────────────
build_edge_cards(
  data                = actionable_q1pts_top,
  player_col          = "scorer",
  last_col            = "last_game_q1pts",
  threshold_label_col = "threshold_label",
  prefix              = "total_pts_",
  title_label         = "pts",
  stat_type           = "pts",
  period = "Q1",
  last_label          = "L5 Avg Q1 Pts"
)
```


### Assists

```{r edge_cards_ast, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_q1ast_top,
  player_col          = "assister",
  last_col            = "last_game_q1ast",
  threshold_label_col = "threshold_label",
  prefix              = "total_ast_",
  title_label         = "ast",
  stat_type           = "ast",
  period = "Q1",
  last_label          = "L5 Avg Q1 Ast"
)
```


### Rebounds

```{r edge_cards_reb, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_q1reb_top,
  player_col          = "rebounder",
  last_col            = "last_game_q1reb",
  threshold_label_col = "threshold_label",
  prefix              = "total_reb_",
  title_label         = "reb",
  stat_type           = "reb",
  period = "Q1",
  last_label          = "L5 Avg Q1 Reb"
)
```


H1 {data-navmenu="Test"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r edge_cards_h1pts, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_h1pts_top,
  player_col          = "scorer",
  last_col            = "last_game_h1pts",
  threshold_label_col = "threshold_label",
  prefix              = "total_pts_",
  title_label         = "pts",
  stat_type           = "pts",
  period = "H1",
  last_label          = "L5 Avg H1 Pts"
)
```



### Assists

```{r edge_cards_h1ast, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_h1ast_top,
  player_col          = "assister",
  last_col            = "last_game_h1ast",
  threshold_label_col = "threshold_label",
  prefix              = "total_ast_",
  title_label         = "ast",
  stat_type           = "ast",
  period = "H1",
  last_label          = "L5 Avg H1 Ast"
)
```


### Rebounds

```{r edge_cards_h1reb, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_h1reb_top,
  player_col          = "rebounder",
  last_col            = "last_game_h1reb",
  threshold_label_col = "threshold_label",
  prefix              = "total_reb_",
  title_label         = "reb",
  stat_type           = "reb",
  period = "H1",
  last_label          = "L5 Avg H1 Reb"
)
```


Q3 {data-navmenu="Test"}
=======================================================================

Row {.tabset .tabset-fade .tabset-pills data-height=1000}
-----------------------------------------------------------------------

### Points

```{r edge_cards_q3pts, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_q3pts_top,
  player_col          = "scorer",
  last_col            = "last_game_q3pts",
  threshold_label_col = "threshold_label",
  prefix              = "total_pts_",
  
  title_label         = "pts",
  stat_type           = "pts",
  period = "Q3",
  last_label          = "L5 Avg Q3 Pts"
)
```


### Assists

```{r edge_cards_q3ast, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_q3ast_top,
  player_col          = "assister",
  last_col            = "last_game_q3ast",
  threshold_label_col = "threshold_label",
  prefix              = "total_ast_",
  
  title_label         = "ast",
  stat_type           = "ast",
  period = "Q3",
  last_label          = "L5 Avg Q3 Ast"
)
```


### Rebounds

```{r edge_cards_q3reb, echo=FALSE, warning=FALSE, message=FALSE}
build_edge_cards(
  data                = actionable_q3reb_top,
  player_col          = "rebounder",
  last_col            = "last_game_q3reb",
  threshold_label_col = "threshold_label",
  prefix              = "total_reb_",
  
  title_label         = "reb",
  stat_type           = "reb",
  period = "Q3",
  last_label          = "L5 Avg Q3 Reb"
)
```